---
title: "Analysis of flowering photoperiod and predictor variables"
output: html_document
---

Main Analyses for Jagdish et al. (In Review) - Shining a light on patterns of photoperiod sensitivty in seed germination across latitudes, ecosystems and functional traits

- see Rmarkdown "BayesianPhotoperiodMetricOfficial.Rmd" for gaining a photoperiod sensitivity index for each species using bayesian GLMs
- see Rmarkdown file "PhylogeneticAnalysis.Rmd" for Phylogenetic Analyses of photoperiod sensitivity across our species
- see Rmarkdown file "MainAnalyses.Rmd" for main analysis of germination photoperiod sensitivity and it's relationship with all environmental/ecological predictor variables

This code analyses the categorical response variable photoperiod sensitivity - (long day, short day or non-sensitive to photoperiod) logistically regressed against against environmental predictor variables - latitude, Leaf area index, habitat and the ecological variable - seed mass

Step 1: Install all relevant libraries
```{r}
library(lme4)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(rcompanion)
library(emmeans)
library(rstatix)
library(ggpubr)
library(Hmisc)
```


Step 2: read in data

```{r}
globalfloweringphotoperiod <- read.csv("photoperiod_global_addition.csv")

#add a column for general photoperiod sensitivity irrespective of whether the species is short day or long day

globalfloweringphotoperiod <- globalfloweringphotoperiod %>%
  mutate(OverallPS = case_when(photoperiodism == 'na' ~ '0',
                               photoperiodism == 'ld' ~ '1',
                               photoperiodism == 'sd' ~ '1',
                               photoperiodism == 'sld' ~ '1',
                               photoperiodism == 'yes' ~ '1')) %>%
  mutate(SDLD = case_when(photoperiodism == 'na' ~ 'NA',
                               photoperiodism == 'ld' ~ '0',
                               photoperiodism == 'sd' ~ '1',
                               photoperiodism == 'sld' ~ 'NA',
                               photoperiodism == 'yes' ~ 'NA'))

globalfloweringphotoperiod$OverallPS <- as.numeric(globalfloweringphotoperiod$OverallPS)
globalfloweringphotoperiod$SDLD <- as.numeric(globalfloweringphotoperiod$SDLD)
```


Step 3: Running the models

PART 1:

#FLOWERING PHOTOPERIOD SENSITIVITY AND LATITUDE

A) I) The 'Original' model (prior to classifying species as long-day sensitive, short-day sensitive, or neither: 
```{r}
latitudemodel <- glm(OverallPS ~ lat, family = "binomial", data = globalfloweringphotoperiod)

summary(latitudemodel)
plot(latitudemodel)
```

A. II) Model comparing latitude and LD/SD:
```{r}
latitudemodelLDSD <- glm(OverallPS~SDLD + lat + SDLD * lat, family = gaussian(link = "identity"), data =globalfloweringphotoperiod)

summary(latitudemodelLDSD)
plot(latitudemodelLDSD)
```

B) I) Plot of 'Original':
```{r}
latitudeplot <- ggplot(aes(x=lat, y=as.factor(OverallPS)), data=globalfloweringphotoperiod) +
  geom_violin(fill = "skyblue", color="skyblue", size = 0.5) + 
  stat_summary(fun.data='mean_sd', color='black') +
  theme_classic() + 
  labs(x = "Latitude (°S)", y = "Photoperiod Sensitivity Index") + 
  theme(axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(latitudeplot)

ggsave(latitudeplot, 
       filename = "latitudeplot.jpg",
       width = 7,
       height = 7,
       dpi=600)
```

#Nagelkerke Pseudo R^2 values for the 'Original' model 
```{r}
nagelkerke(latitudemodel)
```

#Nagelkerke Pseudo R^2 values for the LD/SD model:
```{r}
nagelkerke(latitudemodelLDSD)
```

PART 2:

#PHOTOPERIOD SENSITIVITY IN FLOWERING TIME AND SEED MASS

A) I) The 'Original' seed mass model:
```{r}
seedmassmodel <- glm(OverallPS ~ log10(seed_mass), family = "binomial", data = globalfloweringphotoperiod)

summary(seedmassmodel)
plot(seedmassmodel)
```

A) II) The 'Original' seed mass model log10 transformed x-axis:
```{r}
seedmassplot <- ggplot(aes(x=(seed_mass), y=(as.factor(OverallPS))), data=globalfloweringphotoperiod) +
  geom_violin(color = "skyblue", fill = "skyblue", size =4) + 
  stat_summary(fun.data='mean_sd', color='black') +
  theme_classic() + scale_x_continuous(trans='log10') + 
  xlab(expression(Seed~Mass~(mg)~(Log["10"]~Scale))) + 
  labs(y = "Photoperiod Sensitivity Index") + theme(
  axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(seedmassplot)

ggsave(seedmassplot, 
       filename = "seedmassplot.jpg",
       width = 7,
       height = 7,
       dpi=600)
```

B. I) Seed Mass and LD/SD:
```{r}
seedmassmodelLDSD <- glm(OverallPS~SDLD + seed_mass + SDLD * seed_mass, family = gaussian(link = "identity"), data =globalfloweringphotoperiod)

summary(seedmassmodelLDSD)
plot(seedmassmodelLDSD)
```

#Nagelkerke Pseudo-R^2 value for 'Original':
```{r}
nagelkerke(seedmassmodel)
```

#Nagelkerke Pseudo-R^2 value for Seed Mass and LD/SD:

```{r}
nagelkerke (seedmassmodelLDSD)
```

PART 3:

#FLOWERING PHOTOPERIOD SENSITIVITY AND LEAF AREA INDEX

A) The original LAI model 
```{r}
LAImodel <- glm(OverallPS ~ LAI, family = "binomial", data = globalfloweringphotoperiod)
summary(LAImodel)
plot(LAImodel)
```

B. LAI and LD/SD: 

```{r}
LAILDSD <- glm(OverallPS~SDLD + LAI + SDLD * LAI, family = gaussian(link = "identity"), data =globalfloweringphotoperiod)

summary(LAILDSD)
```
Nagelkerke Pseudo-R^2 value for 'Original':
```{r}
nagelkerke(LAImodel)
```
Nagelkerke Pseudo-R^2 value for LAI and LD/SD:

```{r}
nagelkerke (LAILDSD)
```

C. Plot LAI vs photoperiod

```{r}
LAIfloweringphoto <- ggplot(aes(x=(LAI), y=(as.factor(OverallPS))), data=globalfloweringphotoperiod) +
  geom_violin(color = "skyblue", fill = "skyblue", size =4) + 
  stat_summary(fun.data='mean_sd', color='black') +
  theme_classic() + 
  labs(y = "Photoperiod Sensitivity Index", x = "LAI") + 
  theme(axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(LAIfloweringphoto)

ggsave(LAIfloweringphoto, 
       filename = "LAIfloweringphoto.jpg",
       width = 7,
       height = 7,
       dpi=600)
```


PART 4:

#FLOWERING PHOTOPERIOD AND ALPINE VS NON-ALPINE ENVIRONMENT 

A) The original alpine model 
```{r}
ALPINEmodel <- glm(OverallPS ~ alpine, family = "binomial", data = globalfloweringphotoperiod)
summary(ALPINEmodel)
plot(ALPINEmodel)
```

B. Alpine/non-alpine and LD/SD: 

```{r}
ALPINELDSD <- glm(OverallPS~SDLD + alpine + SDLD * alpine, family = gaussian(link = "identity"), data =globalfloweringphotoperiod)

summary(ALPINELDSD)
```
Nagelkerke Pseudo-R^2 value for 'Original':
```{r}
nagelkerke(ALPINEmodel)
```
Nagelkerke Pseudo-R^2 value for LAI and LD/SD:

```{r}
nagelkerke (ALPINELDSD)
```

C. Plot ALPINE vs photoperiod

```{r}
ALPINEfloweringphoto <- ggplot(aes(x=(alpine), y=(as.factor(OverallPS))), data=globalfloweringphotoperiod) +
  geom_violin(color = "skyblue", fill = "skyblue", size =4) + 
  stat_summary(fun.data='mean_sd', color='black') +
  theme_classic() + 
  labs(y = "Photoperiod Sensitivity Index", x = "Alpine") + 
  theme(axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(ALPINEfloweringphoto)

ggsave(ALPINEfloweringphoto, 
       filename = "ALPINEfloweringphoto.jpg",
       width = 7,
       height = 7,
       dpi=600)
```


