---
title: "Bayesian Photoperiod Metric"
author: "Ashika Jagdish"
date: "27/08/2020"
output: html_document
---
Bayesian Photoperiod Sensitivity Metric:

In this segment we will code the Bayesian Photoperiod Sensitivity Metric and standard error for each species. This metric will be used in further analyses in the following files:

- see Rmarkdown file "PhylogeneticAnalysis.Rmd" for Phylogenetic Analyses of photoperiod sensitivity across our species
- see Rmarkdown file "MainAnalyses.Rmd" for main analysis of germination photoperiod sensitivity and it's relationship with all environmental/ecological predictor variables

Some notes:
The unedited data from RawBinaryGermData.csv is used for this analysis
The 'emmeans' function compares p-values between treatment groups
Final main analyses only includes 67 angiosperm species (spanning 42 genera and 26 families), due to insufficient germination across other species 

Step 1: Read in raw data
```{r}
RawBinaryGermData <- read.csv("RawBinaryGermData.csv")
```

Step2: Install/open all relevant packages
```{r}
library(dplyr)
library(tidyverse)
library(mvtnorm)
library(arm)
library(emmeans)
```

Step 3: Running the BayesGLM functions (Function 1, which creates a Bayes Generalised Linear Model) and then running Function 2, which uses this BayesGLM to give us a photoperiod metric.

```{r}
#FUNCTION 1
Sensitivitymodel <- function(speciesselected, ...) {
  bayesglm(No.Germinated~Treatment, family=binomial(), data = subset(RawBinaryGermData, Species==speciesselected), prior.scale=2.5)
}

#FUNCTION 2
Sensitivitymetric <- function(model) {
  sqrt((model$coefficients[2]^2+ model$coefficients[3]^2 + (model$coefficients[3]- model$coefficients[2])^2)/3)
}

#You need this line for the third section (to calculate sensitivity)
Sensitivity_Metric_rep_parboot = c()
```

Step 3: Now that we have run these functions, we are going to run them on each species to get our Sensitivity Metric as well as the standard error. Then you want to print them out so we can add it into our "LessThan5" formerly "UpdatedPPDATA" Sheet (that we will use for our weighted regressions). 

Note to self: The Standard error should equal the standard deviation. SE tells us how accurate the mean of any sample population is to the true population. Higher values of SE decreases overall accuracy. 

Note to self: Increase the boostrap replicates to 1:10000 to give it a more stable value 

Note to self: The default prior value of 2.5 is taken from Gemlman et al. (2008) and is appropriate as it is not overly restrictive (like 1) and is a suitbale weight for large treatment changes. In Bayesian statistics, the data is more logical and structured as we "update our beliefs, i.e. prior" as we get more information. 

Species:
1. Acacia leptoloba
```{r}
#getting sensitivity metric
Acacialeptolobamodel <- Sensitivitymodel(speciesselected = "Acacia leptoloba") #first run the model
Acacialeptolobasensitivity <- Sensitivitymetric(model = Acacialeptolobamodel) #then extract the sensitivity metric

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Acacialeptolobamodel$coefficients, sigma = vcov(Acacialeptolobamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AcacialeptolobaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Acacialeptolobasensitivity) #save this number
print(AcacialeptolobaSE) #save this number

summary(Acacialeptolobamodel)
```

```{r}
Acacialeptoloba.emmeans <- emmeans(Acacialeptolobamodel, "Treatment", type = "response")
pairs(Acacialeptoloba.emmeans)
```

2. Acacia ulicifolia
```{r}
#getting sensitivity metric
Acaciaulicifoliamodel <- Sensitivitymodel(speciesselected = "Acacia ulicifolia") #first run the model
Acaciaulicifoliasensitivity <- Sensitivitymetric(model = Acaciaulicifoliamodel) #then extract the sensitivity metric

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Acaciaulicifoliamodel$coefficients, sigma = vcov(Acaciaulicifoliamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AcaciaulicifoliaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Acaciaulicifoliasensitivity) #save this number
print(AcaciaulicifoliaSE) #save this number

summary(Acaciaulicifoliamodel)
```

```{r}
Acaciaulicifolia.emmeans <- emmeans(Acaciaulicifoliamodel, "Treatment")
pairs(Acaciaulicifolia.emmeans)
```

3. Acaena Species A
```{r}
#getting sensitivity metric
Acaenaspamodel <- Sensitivitymodel(speciesselected = "Acaena Species A") #first run the model
Acaenaspasensitivity <- Sensitivitymetric(model = Acaenaspamodel) #then extract the sensitivity metric

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Acaenaspamodel$coefficients, sigma = vcov(Acaenaspamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AcaenaspaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Acaenaspasensitivity) #save this number
print(AcaenaspaSE) #save this number
summary(Acaenaspamodel)
```

```{r}
Acaenaspamodel.emmeans <- emmeans(Acaenaspamodel, "Treatment")
pairs(Acaenaspamodel.emmeans)
```

4. Aciphylla glacialis
```{r}
#getting sensitivity metric
Aciphyllaglacialismodel <- Sensitivitymodel(speciesselected = "Aciphylla glacialis") #first run the model
Aciphyllaglacialissensitivity <- Sensitivitymetric(model = Aciphyllaglacialismodel) #then extract the sensitivity metric

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Aciphyllaglacialismodel$coefficients, sigma = vcov(Aciphyllaglacialismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AciphyllaglacialisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Aciphyllaglacialissensitivity) #save this number
print(AciphyllaglacialisSE) #save this number

```

5. Acradenia euodiiformis
```{r}
#getting sensitivity metric
Acradeniaeuodiiformismodel <- Sensitivitymodel(speciesselected = "Acradenia euodiiformis") 
Acradeniaeuodiiformissensitivity <- Sensitivitymetric(model = Acradeniaeuodiiformismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Acradeniaeuodiiformismodel$coefficients, sigma = vcov(Acradeniaeuodiiformismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AcradeniaeuodiiformisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Acradeniaeuodiiformissensitivity) #save this number
print(AcradeniaeuodiiformisSE) #save this number
```

6. Acronychia crassipetala
```{r}
#getting sensitivity metric
Acronychiacrassipetalamodel <- Sensitivitymodel(speciesselected = "Acronychia crassipetala") 
Acronychiacrassipetalasensitivity <- Sensitivitymetric(model = Acronychiacrassipetalamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Acronychiacrassipetalamodel$coefficients, sigma = vcov(Acronychiacrassipetalamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AcronychiacrassipetalaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Acronychiacrassipetalasensitivity) #save this number
print(AcronychiacrassipetalaSE) #save this number
summary(Acronychiacrassipetalamodel)
```

```{r}
Acronychiacrassipetala.emmeans <- emmeans(Acronychiacrassipetalamodel, "Treatment")
pairs(Acronychiacrassipetala.emmeans)
```

7. Acronychia oblongifolia
```{r}
#getting sensitivity metric
Acronychiaoblongifoliamodel <- Sensitivitymodel(speciesselected = "Acronychia oblongifolia") 
Acronychiaoblongifoliasensitivity <- Sensitivitymetric(model = Acronychiaoblongifoliamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Acronychiaoblongifoliamodel$coefficients, sigma = vcov(Acronychiaoblongifoliamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AcronychiaoblongifoliaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Acronychiaoblongifoliasensitivity) #save this number
print(AcronychiaoblongifoliaSE) #save this number
summary(Acronychiaoblongifoliamodel)
```

```{r}
Acronychiaoblongifolia.emmeans <- emmeans(Acronychiaoblongifoliamodel, "Treatment", type = "response")
pairs(Acronychiaoblongifolia.emmeans)
```

8. Acrothamnus hookeri
```{r}
#getting sensitivity metric
Acrothamnushookerimodel <- Sensitivitymodel(speciesselected = "Acrothamnus hookeri") 
Acrothamnushookerisensitivity <- Sensitivitymetric(model = Acrothamnushookerimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Acrothamnushookerimodel$coefficients, sigma = vcov(Acrothamnushookerimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AcrothamnushookeriSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Acrothamnushookerisensitivity) #save this number
print(AcrothamnushookeriSE) #save this number
```

9. Alchornea ilicifolia
```{r}
#getting sensitivity metric
Alchorneailicifoliamodel <- Sensitivitymodel(speciesselected = "Alchornea ilicifolia") 
Alchorneailicifoliasensitivity <- Sensitivitymetric(model = Alchorneailicifoliamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Alchorneailicifoliamodel$coefficients, sigma = vcov(Alchorneailicifoliamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AlchorneailicifoliaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Alchorneailicifoliasensitivity) #save this number
print(AlchorneailicifoliaSE) #save this number
```

10. Allocasuarina littoralis
```{r}
#getting sensitivity metric
Allocasuarinalittoralismodel <- Sensitivitymodel(speciesselected = "Allocasuarina littoralis") 
Allocasuarinalittoralissensitivity <- Sensitivitymetric(model = Allocasuarinalittoralismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Allocasuarinalittoralismodel$coefficients, sigma = vcov(Allocasuarinalittoralismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AllocasuarinalittoralisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Allocasuarinalittoralissensitivity) #save this number
print(AllocasuarinalittoralisSE) #save this number
summary(Allocasuarinalittoralismodel)
```

```{r}
Allocasuarinalittoralis.emmeans <- emmeans(Allocasuarinalittoralismodel, "Treatment", type = "response")
pairs(Allocasuarinalittoralis.emmeans)
```

11. Alphitonia petrei
```{r}
#getting sensitivity metric
Alphitoniapetreimodel <- Sensitivitymodel(speciesselected = "Alphitonia petrei") 
Alphitoniapetreisensitivity <- Sensitivitymetric(model = Alphitoniapetreimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Alphitoniapetreimodel$coefficients, sigma = vcov(Alphitoniapetreimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AlphitoniapetreiSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Alphitoniapetreisensitivity) #save this number
print(AlphitoniapetreiSE) #save this number
```

12. Alpinia arctiflora
```{r}
#getting sensitivity metric
Alpiniaarctifloramodel <- Sensitivitymodel(speciesselected = "Alpinia arctiflora") 
Alpiniaarctiflorasensitivity <- Sensitivitymetric(model = Alpiniaarctifloramodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Alpiniaarctifloramodel$coefficients, sigma = vcov(Alpiniaarctifloramodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AlpiniaarctifloraSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Alpiniaarctiflorasensitivity) #save this number
print(AlpiniaarctifloraSE) #save this number
summary(Alpiniaarctifloramodel)
```

```{r}
Alpiniaarctiflora.emmeans <- emmeans(Alpiniaarctifloramodel, "Treatment")
pairs(Alpiniaarctiflora.emmeans)
```

13. Alpinia caerulea
```{r}
#getting sensitivity metric
Alpiniacaeruleamodel <- Sensitivitymodel(speciesselected = "Alpinia caerulea") 
Alpiniacaeruleasensitivity <- Sensitivitymetric(model = Alpiniacaeruleamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Alpiniacaeruleamodel$coefficients, sigma = vcov(Alpiniacaeruleamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AlpiniacaeruleaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Alpiniacaeruleasensitivity) #save this number
print(AlpiniacaeruleaSE) #save this number
summary(Alpiniacaeruleamodel)
```

```{r}
Alpiniacaerulea.emmeans <- emmeans(Alpiniacaeruleamodel, "Treatment")
pairs(Alpiniacaerulea.emmeans)
```

14. Austrosteenisia blackii
```{r}
#getting sensitivity metric
Austrosteenisiablackiimodel <- Sensitivitymodel(speciesselected = "Austrosteenisia blackii") 
Austrosteenisiablackiisensitivity <- Sensitivitymetric(model = Austrosteenisiablackiimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Austrosteenisiablackiimodel$coefficients, sigma = vcov(Austrosteenisiablackiimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
AustrosteenisiablackiiSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Austrosteenisiablackiisensitivity) #save this number
print(AustrosteenisiablackiiSE) #save this number
summary(Austrosteenisiablackiimodel)
```

```{r}
Austrosteenisiablackii.emmeans <- emmeans(Austrosteenisiablackiimodel, "Treatment")
pairs(Austrosteenisiablackii.emmeans)
```

15. Banksia aemula
```{r}
#getting sensitivity metric
Banksiaaemulamodel <- Sensitivitymodel(speciesselected = "Banksia aemula") 
Banksiaaemulasensitivity <- Sensitivitymetric(model = Banksiaaemulamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Banksiaaemulamodel$coefficients, sigma = vcov(Banksiaaemulamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
BanksiaaemulaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Banksiaaemulasensitivity) #save this number
print(BanksiaaemulaSE) #save this number
summary(Banksiaaemulamodel)
```

```{r}
Banksiaaemula.emmeans <- emmeans(Banksiaaemulamodel, "Treatment")
pairs(Banksiaaemula.emmeans)
```

16. Banksia oblongifolia
```{r}
#getting sensitivity metric
Banksiaoblongifoliamodel <- Sensitivitymodel(speciesselected = "Banksia oblongifolia") 
Banksiaoblongifoliasensitivity <- Sensitivitymetric(model = Banksiaoblongifoliamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Banksiaoblongifoliamodel$coefficients, sigma = vcov(Banksiaoblongifoliamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
BanksiaoblongifoliaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Banksiaoblongifoliasensitivity) #save this number
print(BanksiaoblongifoliaSE) #save this number
summary(Banksiaoblongifoliamodel)
```

```{r}
Banksiaoblongifolia.emmeans <- emmeans(Banksiaoblongifoliamodel, "Treatment")
pairs(Banksiaoblongifolia.emmeans)
```

17. Banksia serrata
```{r}
#getting sensitivity metric
Banksiaserratamodel <- Sensitivitymodel(speciesselected = "Banksia serrata") 
Banksiaserratasensitivity <- Sensitivitymetric(model = Banksiaserratamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Banksiaserratamodel$coefficients, sigma = vcov(Banksiaserratamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
BanksiaserrataSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Banksiaserratasensitivity) #save this number
print(BanksiaserrataSE) #save this number
summary(Banksiaserratamodel)
```

```{r}
Banksiaserrata.emmeans <- emmeans(Banksiaserratamodel, "Treatment")
pairs(Banksiaserrata.emmeans)
```

18.  Breynia cernua
```{r}
#getting sensitivity metric
Breyniacernuamodel <- Sensitivitymodel(speciesselected = "Breynia cernua") 
Breyniacernuasensitivity <- Sensitivitymetric(model = Breyniacernuamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Breyniacernuamodel$coefficients, sigma = vcov(Breyniacernuamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
BreyniacernuaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Breyniacernuasensitivity) #save this number
print(BreyniacernuaSE) #save this number
summary(Breyniacernuamodel)
```

```{r}
Breyniacernua.emmeans <- emmeans(Breyniacernuamodel, "Treatment")
pairs(Breyniacernua.emmeans)
```

19. Breynia oblongifolia
```{r}
#getting sensitivity metric
Breyniaoblongifoliamodel <- Sensitivitymodel(speciesselected = "Breynia oblongifolia") 
Breyniaoblongifoliasensitivity <- Sensitivitymetric(model = Breyniaoblongifoliamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Breyniaoblongifoliamodel$coefficients, sigma = vcov(Breyniaoblongifoliamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
BreyniaoblongifoliaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Breyniaoblongifoliasensitivity) #save this number
print(BreyniaoblongifoliaSE) #save this number
```

20. Bursaria spinosa
```{r}
#getting sensitivity metric
Bursariaspinosamodel <- Sensitivitymodel(speciesselected = "Bursaria spinosa") 
Bursariaspinosasensitivity <- Sensitivitymetric(model = Bursariaspinosamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Bursariaspinosamodel$coefficients, sigma = vcov(Bursariaspinosamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
BursariaspinosaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Bursariaspinosasensitivity) #save this number
print(BursariaspinosaSE) #save this number
summary(Bursariaspinosamodel)
```

```{r}
Bursariaspinosa.emmeans <- emmeans(Bursariaspinosamodel, "Treatment")
pairs(Bursariaspinosa.emmeans)
```

21. Callistemon sieberi 
```{r}
#getting sensitivity metric
Callistemonsieberimodel <- Sensitivitymodel(speciesselected = "Callistemon sieberi") 
Callistemonsieberisensitivity <- Sensitivitymetric(model = Callistemonsieberimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Callistemonsieberimodel$coefficients, sigma = vcov(Callistemonsieberimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CallistemonsieberiSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Callistemonsieberisensitivity) #save this number
print(CallistemonsieberiSE) #save this number
summary(Callistemonsieberimodel) 
```

```{r}
Callistemonsieberi.emmeans <- emmeans(Callistemonsieberimodel, "Treatment")
pairs(Callistemonsieberi.emmeans)
```

22. Callitris intratropica
```{r}
#getting sensitivity metric
Callitrisintratropicamodel <- Sensitivitymodel(speciesselected = "Callitris intratropica") 
Callitrisintratropicasensitivity <- Sensitivitymetric(model = Callitrisintratropicamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Callitrisintratropicamodel$coefficients, sigma = vcov(Callitrisintratropicamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CallitrisintratropicaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Callitrisintratropicasensitivity) #save this number
print(CallitrisintratropicaSE) #save this number
```

23. Carpha nivicola
```{r}
#getting sensitivity metric
Carphanivicolamodel <- Sensitivitymodel(speciesselected = "Carpha nivicola") 
Carphanivicolasensitivity <- Sensitivitymetric(model = Carphanivicolamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Carphanivicolamodel$coefficients, sigma = vcov(Carphanivicolamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CarphanivicolaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Carphanivicolasensitivity) #save this number
print(CarphanivicolaSE) #save this number
```

24. Celmisia longifolia
```{r}
#getting sensitivity metric
Celmisialongifoliamodel <- Sensitivitymodel(speciesselected = "Celmisia longifolia") 
Celmisialongifoliasensitivity <- Sensitivitymetric(model = Celmisialongifoliamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Celmisialongifoliamodel$coefficients, sigma = vcov(Celmisialongifoliamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CelmisialongifoliaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Celmisialongifoliasensitivity) #save this number
print(CelmisialongifoliaSE) #save this number
summary(Celmisialongifoliamodel)
```

```{r}
Celmisialongifolia.emmeans <- emmeans(Celmisialongifoliamodel, "Treatment")
pairs(Celmisialongifolia.emmeans)
```

25. Chamaecrista concinna
```{r}
#getting sensitivity metric
Chamaecristaconcinnamodel <- Sensitivitymodel(speciesselected = "Chamaecrista concinna") 
Chamaecristaconcinnasensitivity <- Sensitivitymetric(model = Chamaecristaconcinnamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Chamaecristaconcinnamodel$coefficients, sigma = vcov(Chamaecristaconcinnamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
ChamaecristaconcinnaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Chamaecristaconcinnasensitivity) #save this number
print(ChamaecristaconcinnaSE) #save this number
summary(Chamaecristaconcinnamodel)
```

```{r}
Chamaecristaconcinna.emmeans <- emmeans(Chamaecristaconcinnamodel, "Treatment")
pairs(Chamaecristaconcinna.emmeans)
```

26. Chionochloa frigida
```{r}
#getting sensitivity metric
Chionochloafrigidamodel <- Sensitivitymodel(speciesselected = "Chionochloa frigida") 
Chionochloafrigidasensitivity <- Sensitivitymetric(model = Chionochloafrigidamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Chionochloafrigidamodel$coefficients, sigma = vcov(Chionochloafrigidamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
ChionochloafrigidaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Chionochloafrigidasensitivity) #save this number
print(ChionochloafrigidaSE) #save this number
summary(Chionochloafrigidamodel)
```

```{r}
Chionochloafrigida.emmeans <- emmeans(Chionochloafrigidamodel, "Treatment")
pairs(Chionochloafrigida.emmeans)
```

27. Cissus antarctica
```{r}
#getting sensitivity metric
Cissusantarcticamodel <- Sensitivitymodel(speciesselected = "Cissus antarctica") 
Cissusantarcticasensitivity <- Sensitivitymetric(model = Cissusantarcticamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Cissusantarcticamodel$coefficients, sigma = vcov(Cissusantarcticamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CissusantarcticaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Cissusantarcticasensitivity) #save this number
print(CissusantarcticaSE) #save this number
```

28. Cissus hypoglauca.B
#This species was collected from Border Ranges National Park
```{r}
#getting sensitivity metric
Cissushypoglauca.Bmodel <- Sensitivitymodel(speciesselected = "Cissus hypoglauca.B") 
Cissushypoglauca.Bsensitivity <- Sensitivitymetric(model = Cissushypoglauca.Bmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Cissushypoglauca.Bmodel$coefficients, sigma = vcov(Cissushypoglauca.Bmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Cissushypoglauca.BSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Cissushypoglauca.Bsensitivity) #save this number
print(Cissushypoglauca.BSE) #save this number
```

29. Cissus hypoglauca.D
#This species was collected from Dorrigo National Park
```{r}
#getting sensitivity metric
Cissushypoglauca.Dmodel <- Sensitivitymodel(speciesselected = "Cissus hypoglauca.D") 
Cissushypoglauca.Dsensitivity <- Sensitivitymetric(model = Cissushypoglauca.Dmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Cissushypoglauca.Dmodel$coefficients, sigma = vcov(Cissushypoglauca.Dmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Cissushypoglauca.DSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Cissushypoglauca.Dsensitivity) #save this number
print(Cissushypoglauca.DSE) #save this number
summary(Cissushypoglauca.Dmodel)
```

```{r}
Cissushypoglauca.D.emmeans <- emmeans(Cissushypoglauca.Dmodel, "Treatment")
pairs(Cissushypoglauca.D.emmeans)
```

30. Cissus hypoglauca.M
#This species was collected from Mallanganee National Park
```{r}
#getting sensitivity metric
Cissushypoglauca.Mmodel <- Sensitivitymodel(speciesselected = "Cissus hypoglauca.M") 
Cissushypoglauca.Msensitivity <- Sensitivitymetric(model = Cissushypoglauca.Mmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Cissushypoglauca.Mmodel$coefficients, sigma = vcov(Cissushypoglauca.Mmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Cissushypoglauca.MSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Cissushypoglauca.Msensitivity) #save this number
print(Cissushypoglauca.MSE) #save this number
```

31. Cordyline petiolaris 
```{r}
#getting sensitivity metric
Cordylinepetiolarismodel <- Sensitivitymodel(speciesselected = "Cordyline petiolaris") 
Cordylinepetiolarissensitivity <- Sensitivitymetric(model = Cordylinepetiolarismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Cordylinepetiolarismodel$coefficients, sigma = vcov(Cordylinepetiolarismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CordylinepetiolarisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Cordylinepetiolarissensitivity) #save this number
print(CordylinepetiolarisSE) #save this number
```

32. Coronidium boormanii
```{r}
#getting sensitivity metric
Coronidiumboormaniimodel <- Sensitivitymodel(speciesselected = "Coronidium boormanii") 
Coronidiumboormaniisensitivity <- Sensitivitymetric(model = Coronidiumboormaniimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Coronidiumboormaniimodel$coefficients, sigma = vcov(Coronidiumboormaniimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CoronidiumboormaniiSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Coronidiumboormaniisensitivity) #save this number
print(CoronidiumboormaniiSE) #save this number
summary(Coronidiumboormaniimodel)
```

```{r}
Coronidiumboormanii.emmeans <- emmeans(Coronidiumboormaniimodel, "Treatment")
pairs(Coronidiumboormanii.emmeans)
```

33. Coronidium scorpiodes
```{r}
#getting sensitivity metric
Coronidiumscorpiodesmodel <- Sensitivitymodel(speciesselected = "Coronidium scorpiodes") 
Coronidiumscorpiodessensitivity <- Sensitivitymetric(model = Coronidiumscorpiodesmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Coronidiumscorpiodesmodel$coefficients, sigma = vcov(Coronidiumscorpiodesmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CoronidiumscorpiodesSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Coronidiumscorpiodessensitivity) #save this number
print(CoronidiumscorpiodesSE) #save this number
summary(Coronidiumscorpiodesmodel)
```

```{r}
Coronidiumscorpiodes.emmeans <- emmeans(Coronidiumscorpiodesmodel, "Treatment")
pairs(Coronidiumscorpiodes.emmeans)
```

34. Croton insularis
```{r}
#getting sensitivity metric
Crotoninsularismodel <- Sensitivitymodel(speciesselected = "Croton insularis") 
Crotoninsularissensitivity <- Sensitivitymetric(model = Crotoninsularismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Crotoninsularismodel$coefficients, sigma = vcov(Crotoninsularismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CrotoninsularisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Crotoninsularissensitivity) #save this number
print(CrotoninsularisSE) #save this number
summary(Crotoninsularismodel)
```

```{r}
Crotoninsularis.emmeans <- emmeans(Crotoninsularismodel, "Treatment")
pairs(Crotoninsularis.emmeans)
```

35. Cryptocarya microneura
```{r}
#getting sensitivity metric
Cryptocaryamicroneuramodel <- Sensitivitymodel(speciesselected = "Cryptocarya microneura") 
Cryptocaryamicroneurasensitivity <- Sensitivitymetric(model = Cryptocaryamicroneuramodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Cryptocaryamicroneuramodel$coefficients, sigma = vcov(Cryptocaryamicroneuramodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CryptocaryamicroneuraSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Cryptocaryamicroneurasensitivity) #save this number
print(CryptocaryamicroneuraSE) #save this number
```

36. Cupaniopsis flagelliformis
```{r}
#getting sensitivity metric
Cupaniopsisflagelliformismodel <- Sensitivitymodel(speciesselected = "Cupaniopsis flagelliformis") 
Cupaniopsisflagelliformissensitivity <- Sensitivitymetric(model = Cupaniopsisflagelliformismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Cupaniopsisflagelliformismodel$coefficients, sigma = vcov(Cupaniopsisflagelliformismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
CupaniopsisflagelliformisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Cupaniopsisflagelliformissensitivity) #save this number
print(CupaniopsisflagelliformisSE) #save this number
summary(Cupaniopsisflagelliformismodel)
```

```{r}
Cupaniopsisflagelliformis.emmeans <- emmeans(Cupaniopsisflagelliformismodel, "Treatment")
pairs(Cupaniopsisflagelliformis.emmeans)
```

37. Ehretia acuminata
```{r}
#getting sensitivity metric
Ehretiaacuminatamodel <- Sensitivitymodel(speciesselected = "Ehretia acuminata") 
Ehretiaacuminatasensitivity <- Sensitivitymetric(model = Ehretiaacuminatamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Ehretiaacuminatamodel$coefficients, sigma = vcov(Ehretiaacuminatamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EhretiaacuminataSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Ehretiaacuminatasensitivity) #save this number
print(EhretiaacuminataSE) #save this number
```

38. Einadia nutans 
```{r}
#getting sensitivity metric
Einadianutansmodel <- Sensitivitymodel(speciesselected = "Einadia nutans") 
Einadianutanssensitivity <- Sensitivitymetric(model = Einadianutansmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Einadianutansmodel$coefficients, sigma = vcov(Einadianutansmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EinadianutansSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Einadianutanssensitivity) #save this number
print(EinadianutansSE) #save this number
summary(Einadianutansmodel)
```

```{r}
Einadianutans.emmeans <- emmeans(Einadianutansmodel, "Treatment")
pairs(Einadianutans.emmeans)
```

39. Epacris microphylla
```{r}
#getting sensitivity metric
Epacrismicrophyllamodel <- Sensitivitymodel(speciesselected = "Epacris microphylla") 
Epacrismicrophyllasensitivity <- Sensitivitymetric(model = Epacrismicrophyllamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Epacrismicrophyllamodel$coefficients, sigma = vcov(Epacrismicrophyllamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EpacrismicrophyllaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Epacrismicrophyllasensitivity) #save this number
print(EpacrismicrophyllaSE) #save this number
```

40. Eucalyptus cloeziana
```{r}
#getting sensitivity metric
Eucalyptuscloezianamodel <- Sensitivitymodel(speciesselected = "Eucalyptus cloeziana") 
Eucalyptuscloezianasensitivity <- Sensitivitymetric(model = Eucalyptuscloezianamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Eucalyptuscloezianamodel$coefficients, sigma = vcov(Eucalyptuscloezianamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EucalyptuscloezianaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Eucalyptuscloezianasensitivity) #save this number
print(EucalyptuscloezianaSE) #save this number
summary(Eucalyptuscloezianamodel)
```

```{r}
Eucalyptuscloeziana.emmeans <- emmeans(Eucalyptuscloezianamodel, "Treatment")
pairs(Eucalyptuscloeziana.emmeans)
```

41. Eucalyptus dalrympleana
```{r}
#getting sensitivity metric
Eucalyptusdalrympleanamodel <- Sensitivitymodel(speciesselected = "Eucalyptus dalrympleana") 
Eucalyptusdalrympleanasensitivity <- Sensitivitymetric(model = Eucalyptusdalrympleanamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Eucalyptusdalrympleanamodel$coefficients, sigma = vcov(Eucalyptusdalrympleanamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EucalyptusdalrympleanaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Eucalyptusdalrympleanasensitivity) #save this number
print(EucalyptusdalrympleanaSE) #save this number
summary(Eucalyptusdalrympleanamodel)
```

```{r}
Eucalyptusdalrympleana.emmeans <- emmeans(Eucalyptusdalrympleanamodel, "Treatment")
pairs(Eucalyptusdalrympleana.emmeans)
```

42. Eucalyptus ebbaneoensis subsp. Ebbanoensis
```{r}
#getting sensitivity metric
Eucalyptusebbaneoensismodel <- Sensitivitymodel(speciesselected = "Eucalyptus ebbaneoensis subsp. Ebbanoensis") 
Eucalyptusebbaneoensissensitivity <- Sensitivitymetric(model = Eucalyptusebbaneoensismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Eucalyptusebbaneoensismodel$coefficients, sigma = vcov(Eucalyptusebbaneoensismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EucalyptusebbaneoensisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Eucalyptusebbaneoensissensitivity) #save this number
print(EucalyptusebbaneoensisSE) #save this number
summary(Eucalyptusebbaneoensismodel)
```

```{r}
Eucalyptusebbaneoensis.emmeans <- emmeans(Eucalyptusebbaneoensismodel, "Treatment")
pairs(Eucalyptusebbaneoensis.emmeans)
```

43. Eucalyptus lockyeri
```{r}
#getting sensitivity metric
Eucalyptuslockyerimodel <- Sensitivitymodel(speciesselected = "Eucalyptus lockyeri") 
Eucalyptuslockyerisensitivity <- Sensitivitymetric(model = Eucalyptuslockyerimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Eucalyptuslockyerimodel$coefficients, sigma = vcov(Eucalyptuslockyerimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EucalyptuslockyeriSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Eucalyptuslockyerisensitivity) #save this number
print(EucalyptuslockyeriSE) #save this number
summary(Eucalyptuslockyerimodel)
```

```{r}
Eucalyptuslockyeri.emmeans <- emmeans(Eucalyptuslockyerimodel, "Treatment")
pairs(Eucalyptuslockyeri.emmeans)
```

44. Eucalyptus pauciflora
```{r}
#getting sensitivity metric
Eucalyptuspaucifloramodel <- Sensitivitymodel(speciesselected = "Eucalyptus pauciflora") 
Eucalyptuspauciflorasensitivity <- Sensitivitymetric(model = Eucalyptuspaucifloramodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Eucalyptuspaucifloramodel$coefficients, sigma = vcov(Eucalyptuspaucifloramodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EucalyptuspaucifloraSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Eucalyptuspauciflorasensitivity) #save this number
print(EucalyptuspaucifloraSE) #save this number
summary(Eucalyptuspaucifloramodel)
```

```{r}
Eucalyptuspauciflora.emmeans <- emmeans(Eucalyptuspaucifloramodel, "Treatment")
pairs(Eucalyptuspauciflora.emmeans) 
```

45. Eucalyptus shirleyi
```{r}
#getting sensitivity metric
Eucalyptusshirleyimodel <- Sensitivitymodel(speciesselected = "Eucalyptus shirleyi") 
Eucalyptusshirleyisensitivity <- Sensitivitymetric(model = Eucalyptusshirleyimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Eucalyptusshirleyimodel$coefficients, sigma = vcov(Eucalyptusshirleyimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EucalyptusshirleyiSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Eucalyptusshirleyisensitivity) #save this number
print(EucalyptusshirleyiSE) #save this number
summary(Eucalyptusshirleyimodel)
```

```{r}
Eucalyptusshirleyi.emmeans <- emmeans(Eucalyptusshirleyimodel, "Treatment")
pairs(Eucalyptusshirleyi.emmeans)
```

46. Eucalyptus websteriana subsp. norsemanica
```{r}
#getting sensitivity metric
Eucalyptuswebsterianamodel <- Sensitivitymodel(speciesselected = "Eucalyptus websteriana subsp. norsemanica") 
Eucalyptuswebsterianasensitivity <- Sensitivitymetric(model = Eucalyptuswebsterianamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Eucalyptuswebsterianamodel$coefficients, sigma = vcov(Eucalyptuswebsterianamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EucalyptuswebsterianaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Eucalyptuswebsterianasensitivity) #save this number
print(EucalyptuswebsterianaSE) #save this number
summary(Eucalyptuswebsterianamodel)
```

```{r}
Eucalyptuswebsteriana.emmeans <- emmeans(Eucalyptuswebsterianamodel, "Treatment")
pairs(Eucalyptuswebsteriana.emmeans)
```

47. Euphrasia collina subsp. diversicolor
```{r}
#getting sensitivity metric
Euphrasiadiversicolormodel <- Sensitivitymodel(speciesselected = "Euphrasia collina subsp. diversicolor") 
Euphrasiadiversicolorsensitivity <- Sensitivitymetric(model = Euphrasiadiversicolormodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Euphrasiadiversicolormodel$coefficients, sigma = vcov(Euphrasiadiversicolormodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
EuphrasiadiversicolorSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Euphrasiadiversicolorsensitivity) #save this number
print(EuphrasiadiversicolorSE) #save this number
```

48. Ficus benjamina
```{r}
#getting sensitivity metric
Ficusbenjaminamodel <- Sensitivitymodel(speciesselected = "Ficus benjamina") 
Ficusbenjaminasensitivity <- Sensitivitymetric(model = Ficusbenjaminamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Ficusbenjaminamodel$coefficients, sigma = vcov(Ficusbenjaminamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
FicusbenjaminaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Ficusbenjaminasensitivity) #save this number
print(FicusbenjaminaSE) #save this number
summary(Ficusbenjaminamodel)
```

```{r}
Ficusbenjamina.emmeans <- emmeans(Ficusbenjaminamodel, "Treatment")
pairs(Ficusbenjamina.emmeans)
```

49. Ganophyllum falcatum
```{r}
#getting sensitivity metric
Ganophyllumfalcatummodel <- Sensitivitymodel(speciesselected = "Ganophyllum falcatum") 
Ganophyllumfalcatumsensitivity <- Sensitivitymetric(model = Ganophyllumfalcatummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Ganophyllumfalcatummodel$coefficients, sigma = vcov(Ganophyllumfalcatummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
GanophyllumfalcatumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Ganophyllumfalcatumsensitivity) #save this number
print(GanophyllumfalcatumSE) #save this number
```

50. Geitonoplesium cymosum
```{r}
#getting sensitivity metric
Geitonoplesiumcymosummodel <- Sensitivitymodel(speciesselected = "Geitonoplesium cymosum") 
Geitonoplesiumcymosumsensitivity <- Sensitivitymetric(model = Geitonoplesiumcymosummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Geitonoplesiumcymosummodel$coefficients, sigma = vcov(Geitonoplesiumcymosummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
GeitonoplesiumcymosumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Geitonoplesiumcymosumsensitivity) #save this number
print(GeitonoplesiumcymosumSE) #save this number
```

51. Glochidion ferdinandi
```{r}
#getting sensitivity metric
Glochidionferdinandimodel <- Sensitivitymodel(speciesselected = "Glochidion ferdinandi") 
Glochidionferdinandisensitivity <- Sensitivitymetric(model = Glochidionferdinandimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Glochidionferdinandimodel$coefficients, sigma = vcov(Glochidionferdinandimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
GlochidionferdinandiSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Glochidionferdinandisensitivity) #save this number
print(GlochidionferdinandiSE) #save this number
summary(Glochidionferdinandimodel)
```

```{r}
Glochidionferdinandi.emmeans <- emmeans(Glochidionferdinandimodel, "Treatment")
pairs(Glochidionferdinandi.emmeans)
```

52. Grevillea glauca
```{r}
#getting sensitivity metric
Grevilleaglaucamodel <- Sensitivitymodel(speciesselected = "Grevillea glauca") 
Grevilleaglaucasensitivity <- Sensitivitymetric(model = Grevilleaglaucamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Grevilleaglaucamodel$coefficients, sigma = vcov(Grevilleaglaucamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
GrevilleaglaucaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Grevilleaglaucasensitivity) #save this number
print(GrevilleaglaucaSE) #save this number
```

53. Hakea dactyloides.R
#This species was collected from Royal National Park- Flat Rock Creek
```{r}
#getting sensitivity metric
Hakeadactyloides.Rmodel <- Sensitivitymodel(speciesselected = "Hakea dactyloides.R") 
Hakeadactyloides.Rsensitivity <- Sensitivitymetric(model = Hakeadactyloides.Rmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Hakeadactyloides.Rmodel$coefficients, sigma = vcov(Hakeadactyloides.Rmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Hakeadactyloides.RSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Hakeadactyloides.Rsensitivity) #save this number
print(Hakeadactyloides.RSE) #save this number
summary(Hakeadactyloides.Rmodel)
```

```{r}
Hakeadactyloides.R.emmeans <- emmeans(Hakeadactyloides.Rmodel, "Treatment")
pairs(Hakeadactyloides.R.emmeans)
```

54. Hakea dactyloides.RC
#This species was collected from Rocky Creek
```{r}
#getting sensitivity metric
Hakeadactyloides.RCmodel <- Sensitivitymodel(speciesselected = "Hakea dactyloides.RC") 
Hakeadactyloides.RCsensitivity <- Sensitivitymetric(model = Hakeadactyloides.RCmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Hakeadactyloides.RCmodel$coefficients, sigma = vcov(Hakeadactyloides.RCmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Hakeadactyloides.RCSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Hakeadactyloides.RCsensitivity) #save this number
print(Hakeadactyloides.RCSE) #save this number
summary(Hakeadactyloides.RCmodel)
```

```{r}
Hakeadactyloides.RC.emmeans <- emmeans(Hakeadactyloides.RCmodel, "Treatment")
pairs(Hakeadactyloides.RC.emmeans)
```

55. Hakea microcarpa
```{r}
#getting sensitivity metric
Hakeamicrocarpamodel <- Sensitivitymodel(speciesselected = "Hakea microcarpa") 
Hakeamicrocarpasensitivity <- Sensitivitymetric(model = Hakeamicrocarpamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Hakeamicrocarpamodel$coefficients, sigma = vcov(Hakeamicrocarpamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
HakeamicrocarpaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Hakeamicrocarpasensitivity) #save this number
print(HakeamicrocarpaSE) #save this number
summary(Hakeamicrocarpamodel)
```

```{r}
Hakeamicrocarpaemmeans <- emmeans(Hakeamicrocarpamodel, "Treatment")
pairs(Hakeamicrocarpaemmeans)
```

56. Hakea sericea
```{r}
#getting sensitivity metric
Hakeasericeamodel <- Sensitivitymodel(speciesselected = "Hakea sericea") 
Hakeasericeasensitivity <- Sensitivitymetric(model = Hakeasericeamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Hakeasericeamodel$coefficients, sigma = vcov(Hakeasericeamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
HakeasericeaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Hakeasericeasensitivity) #save this number
print(HakeasericeaSE) #save this number
summary(Hakeasericeamodel)
```

```{r}
Hakeasericeaemmeans <- emmeans(Hakeasericeamodel, "Treatment")
pairs(Hakeasericeaemmeans)
```

57. Homalanthus populifolius
```{r}
#getting sensitivity metric
Homalanthuspopulifoliusmodel <- Sensitivitymodel(speciesselected = "Homalanthus populifolius") 
Homalanthuspopulifoliussensitivity <- Sensitivitymetric(model = Homalanthuspopulifoliusmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Homalanthuspopulifoliusmodel$coefficients, sigma = vcov(Homalanthuspopulifoliusmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
HomalanthuspopulifoliusSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Homalanthuspopulifoliussensitivity) #save this number
print(HomalanthuspopulifoliusSE) #save this number
```

58. Isotoma anethifolia
```{r}
#getting sensitivity metric
Isotomaanethifoliamodel <- Sensitivitymodel(speciesselected = "Isotoma anethifolia") 
Isotomaanethifoliasensitivity <- Sensitivitymetric(model = Isotomaanethifoliamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Isotomaanethifoliamodel$coefficients, sigma = vcov(Isotomaanethifoliamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
IsotomaanethifoliaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Isotomaanethifoliasensitivity) #save this number
print(IsotomaanethifoliaSE) #save this number
summary(Isotomaanethifoliamodel)
```

```{r}
Isotomaanethifolia.emmeans <- emmeans(Isotomaanethifoliamodel, "Treatment")
pairs(Isotomaanethifolia.emmeans)
```

59. Kunzea ericoides
```{r}
#getting sensitivity metric
Kunzeaericoidesmodel <- Sensitivitymodel(speciesselected = "Kunzea ericoides") 
Kunzeaericoidessensitivity <- Sensitivitymetric(model = Kunzeaericoidesmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Kunzeaericoidesmodel$coefficients, sigma = vcov(Kunzeaericoidesmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
KunzeaericoidesSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Kunzeaericoidessensitivity) #save this number
print(KunzeaericoidesSE) #save this number
summary(Kunzeaericoidesmodel)
```

```{r}
Kunzeaericoides.emmeans <- emmeans(Kunzeaericoidesmodel, "Treatment")
pairs(Kunzeaericoides.emmeans)
```

60. Leptospermum arachnoides
```{r}
#getting sensitivity metric
Larachnoidesmodel <- Sensitivitymodel(speciesselected = "Leptospermum arachnoides") 
Larachnoidessensitivity <- Sensitivitymetric(model = Larachnoidesmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Larachnoidesmodel$coefficients, sigma = vcov(Larachnoidesmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LarachnoidesSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Larachnoidessensitivity) #save this number
print(LarachnoidesSE) #save this number
summary(Larachnoidesmodel)
```

```{r}
Larachnoides.emmeans <- emmeans(Larachnoidesmodel, "Treatment")
pairs(Larachnoides.emmeans)
```

61. Leptospermum grandifolium
```{r}
#getting sensitivity metric
Lgrandifoliummodel <- Sensitivitymodel(speciesselected = "Leptospermum grandifolium") 
Lgrandifoliumsensitivity <- Sensitivitymetric(model = Lgrandifoliummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Lgrandifoliummodel$coefficients, sigma = vcov(Lgrandifoliummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LgrandifoliumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Lgrandifoliumsensitivity) #save this number
print(LgrandifoliumSE) #save this number
summary(Lgrandifoliummodel)
```

```{r}
Lgrandifolium.emmeans <- emmeans(Lgrandifoliummodel, "Treatment")
pairs(Lgrandifolium.emmeans)
```

62. Leptospermum gregarium
```{r}
#getting sensitivity metric
Lgregariummodel <- Sensitivitymodel(speciesselected = "Leptospermum gregarium") 
Lgregariumsensitivity <- Sensitivitymetric(model = Lgregariummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Lgregariummodel$coefficients, sigma = vcov(Lgregariummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LgregariumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Lgregariumsensitivity) #save this number
print(LgregariumSE) #save this number
summary(Lgregariummodel)
```

```{r}
Lgregarium.emmeans <- emmeans(Lgregariummodel, "Treatment")
pairs(Lgregarium.emmeans)
```

63. Leptospermum juniperinum
```{r}
#getting sensitivity metric
Ljuniperinummodel <- Sensitivitymodel(speciesselected = "Leptospermum juniperinum") 
Ljuniperinumsensitivity <- Sensitivitymetric(model = Ljuniperinummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Ljuniperinummodel$coefficients, sigma = vcov(Ljuniperinummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LjuniperinumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Ljuniperinumsensitivity) #save this number
print(LjuniperinumSE) #save this number
summary(Ljuniperinummodel)
```

```{r}
Ljuniperinum.emmeans <- emmeans(Ljuniperinummodel, "Treatment")
pairs(Ljuniperinum.emmeans)
```

64. Leptospermum laevigatum
```{r}
#getting sensitivity metric
Llaevigatummodel <- Sensitivitymodel(speciesselected = "Leptospermum laevigatum") 
Llaevigatumsensitivity <- Sensitivitymetric(model = Llaevigatummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Llaevigatummodel$coefficients, sigma = vcov(Llaevigatummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LlaevigatumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Llaevigatumsensitivity) #save this number
print(LlaevigatumSE) #save this number
summary(Llaevigatummodel)
```

```{r}
Llaevigatum.emmeans <- emmeans(Llaevigatummodel, "Treatment")
pairs(Llaevigatum.emmeans)
```

65. Leptospermum myrtifolium
```{r}
#getting sensitivity metric
Lmyrtifoliummodel <- Sensitivitymodel(speciesselected = "Leptospermum myrtifolium") 
Lmyrtifoliumsensitivity <- Sensitivitymetric(model = Lmyrtifoliummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Lmyrtifoliummodel$coefficients, sigma = vcov(Lmyrtifoliummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LmyrtifoliumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Lmyrtifoliumsensitivity) #save this number
print(LmyrtifoliumSE) #save this number
summary(Lmyrtifoliummodel)
```

```{r}
Lmyrtifolium.emmeans <- emmeans(Lmyrtifoliummodel, "Treatment")
pairs(Lmyrtifolium.emmeans)
```

66. Leptospermum polygafolium
```{r}
#getting sensitivity metric
Lpolygafoliummodel <- Sensitivitymodel(speciesselected = "Leptospermum polygafolium") 
Lpolygafoliumsensitivity <- Sensitivitymetric(model = Lpolygafoliummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Lpolygafoliummodel$coefficients, sigma = vcov(Lpolygafoliummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LpolygafoliumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Lpolygafoliumsensitivity) #save this number
print(LpolygafoliumSE) #save this number
summary(Lpolygafoliummodel)
```

```{r}
Lpolygafolium.emmeans <- emmeans(Lpolygafoliummodel, "Treatment")
pairs(Lpolygafolium.emmeans)
```

67. Leptospermum polygalifolium subsp. montanum
```{r}
#getting sensitivity metric
Lmontanummodel <- Sensitivitymodel(speciesselected = "Leptospermum polygalifolium subsp. montanum") 
Lmontanumsensitivity <- Sensitivitymetric(model = Lmontanummodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Lmontanummodel$coefficients, sigma = vcov(Lmontanummodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LmontanumSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Lmontanumsensitivity) #save this number
print(LmontanumSE) #save this number
summary(Lmontanummodel)
```

```{r}
Lmontanum.emmeans <- emmeans(Lmontanummodel, "Treatment")
pairs(Lmontanum.emmeans)
```

68. Leucochrysum albicans subsp. alpina
```{r}
#getting sensitivity metric
Lalpinamodel <- Sensitivitymodel(speciesselected = "Leucochrysum albicans subsp. alpina") 
Lalpinasensitivity <- Sensitivitymetric(model = Lalpinamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Lalpinamodel$coefficients, sigma = vcov(Lalpinamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
LalpinaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Lalpinasensitivity) #save this number
print(LalpinaSE) #save this number
summary(Lalpinamodel)
```

```{r}
Lalpina.emmeans <- emmeans(Lalpinamodel, "Treatment")
pairs(Lalpina.emmeans)
```

69. Linospadix monostachya.B
#This species was collected from Border Ranges National Park
```{r}
#getting sensitivity metric
Linospadixmonostachya.Bmodel <- Sensitivitymodel(speciesselected = "Linospadix monostachya.B") 
Linospadixmonostachya.Bsensitivity <- Sensitivitymetric(model = Linospadixmonostachya.Bmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Linospadixmonostachya.Bmodel$coefficients, sigma = vcov(Linospadixmonostachya.Bmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Linospadixmonostachya.BSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Linospadixmonostachya.Bsensitivity) #save this number
print(Linospadixmonostachya.BSE) #save this number
summary(Linospadixmonostachya.Bmodel)
```

```{r}
Linospadixmonostachya.B.emmeans <- emmeans(Linospadixmonostachya.Bmodel, "Treatment")
pairs(Linospadixmonostachya.B.emmeans)
```

70. Linospadix monostachya.D
#This species was collected from Dorrigo National Park
```{r}
#getting sensitivity metric
Linospadixmonostachya.Dmodel <- Sensitivitymodel(speciesselected = "Linospadix monostachya.D") 
Linospadixmonostachya.Dsensitivity <- Sensitivitymetric(model = Linospadixmonostachya.Dmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Linospadixmonostachya.Dmodel$coefficients, sigma = vcov(Linospadixmonostachya.Dmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Linospadixmonostachya.DSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Linospadixmonostachya.Dsensitivity) #save this number
print(Linospadixmonostachya.DSE) #save this number
```

71. Maytenus disperma
```{r}
#getting sensitivity metric
Maytenusdispermamodel <- Sensitivitymodel(speciesselected = "Maytenus disperma") 
Maytenusdispermasensitivity <- Sensitivitymetric(model = Maytenusdispermamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Maytenusdispermamodel$coefficients, sigma = vcov(Maytenusdispermamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
MaytenusdispermaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Maytenusdispermasensitivity) #save this number
print(MaytenusdispermaSE) #save this number
```

72. Muehlenbeckia M. sp. Mt Norman
```{r}
#getting sensitivity metric
MuehlenbeckiaNormanmodel <- Sensitivitymodel(speciesselected = "Muehlenbeckia M. sp. Mt Norman") 
MuehlenbeckiaNormansensitivity <- Sensitivitymetric(model = MuehlenbeckiaNormanmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = MuehlenbeckiaNormanmodel$coefficients, sigma = vcov(MuehlenbeckiaNormanmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
MuehlenbeckiaNormanSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(MuehlenbeckiaNormansensitivity) #save this number
print(MuehlenbeckiaNormanSE) #save this number
```

73. Myrsine howittiana
```{r}
#getting sensitivity metric
Myrsinehowittianamodel <- Sensitivitymodel(speciesselected = "Myrsine howittiana") 
Myrsinehowittianasensitivity <- Sensitivitymetric(model = Myrsinehowittianamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Myrsinehowittianamodel$coefficients, sigma = vcov(Myrsinehowittianamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
MyrsinehowittianaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Myrsinehowittianasensitivity) #save this number
print(MyrsinehowittianaSE) #save this number
```

74. Myrsine variabilis
```{r}
#getting sensitivity metric
Myrsinevariabilismodel <- Sensitivitymodel(speciesselected = "Myrsine variabilis") 
Myrsinevariabilissensitivity <- Sensitivitymetric(model = Myrsinevariabilismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Myrsinevariabilismodel$coefficients, sigma = vcov(Myrsinevariabilismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
MyrsinevariabilisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Myrsinevariabilissensitivity) #save this number
print(MyrsinevariabilisSE) #save this number
```

75. Neolitsea dealbata 
```{r}
#getting sensitivity metric
Neolitseadealbatamodel <- Sensitivitymodel(speciesselected = "Neolitsea dealbata") 
Neolitseadealbatasensitivity <- Sensitivitymetric(model = Neolitseadealbatamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Neolitseadealbatamodel$coefficients, sigma = vcov(Neolitseadealbatamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
NeolitseadealbataSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Neolitseadealbatasensitivity) #save this number
print(NeolitseadealbataSE) #save this number
summary(Neolitseadealbatamodel)
```

```{r}
Neolitseadealbata.emmeans <- emmeans(Neolitseadealbatamodel, "Treatment")
pairs(Neolitseadealbata.emmeans)
```

76. Oreomyrrhis ciliata
```{r}
#getting sensitivity metric
Oreomyrrhisciliatamodel <- Sensitivitymodel(speciesselected = "Oreomyrrhis ciliata") 
Oreomyrrhisciliatasensitivity <- Sensitivitymetric(model = Oreomyrrhisciliatamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Oreomyrrhisciliatamodel$coefficients, sigma = vcov(Oreomyrrhisciliatamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
OreomyrrhisciliataSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Oreomyrrhisciliatasensitivity) #save this number
print(OreomyrrhisciliataSE) #save this number
summary(Oreomyrrhisciliatamodel)
```

```{r}
Oreomyrrhisciliata.emmeans <- emmeans(Oreomyrrhisciliatamodel, "Treatment")
pairs(Oreomyrrhisciliata.emmeans)
```

77. Ozothamnus hookeri
```{r}
#getting sensitivity metric
Ozothamnushookerimodel <- Sensitivitymodel(speciesselected = "Ozothamnus hookeri") 
Ozothamnushookerisensitivity <- Sensitivitymetric(model = Ozothamnushookerimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Ozothamnushookerimodel$coefficients, sigma = vcov(Ozothamnushookerimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
OzothamnushookeriSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Ozothamnushookerisensitivity) #save this number
print(OzothamnushookeriSE) #save this number
summary(Ozothamnushookerimodel)
```

```{r}
Ozothamnushookeri.emmeans <- emmeans(Ozothamnushookerimodel, "Treatment")
pairs(Ozothamnushookeri.emmeans)
```

78. Parsonsia induplicata
```{r}
#getting sensitivity metric
Parsonsiainduplicatamodel <- Sensitivitymodel(speciesselected = "Parsonsia induplicata") 
Parsonsiainduplicatasensitivity <- Sensitivitymetric(model = Parsonsiainduplicatamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Parsonsiainduplicatamodel$coefficients, sigma = vcov(Parsonsiainduplicatamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
ParsonsiainduplicataSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Parsonsiainduplicatasensitivity) #save this number
print(ParsonsiainduplicataSE) #save this number
```

79. Petrophile pulchella
```{r}
#getting sensitivity metric
Petrophilepulchellamodel <- Sensitivitymodel(speciesselected = "Petrophile pulchella") 
Petrophilepulchellasensitivity <- Sensitivitymetric(model = Petrophilepulchellamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Petrophilepulchellamodel$coefficients, sigma = vcov(Petrophilepulchellamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
PetrophilepulchellaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Petrophilepulchellasensitivity) #save this number
print(PetrophilepulchellaSE) #save this number
summary(Petrophilepulchellamodel)
```

```{r}
Petrophilepulchella.emmeans <- emmeans(Petrophilepulchellamodel, "Treatment")
pairs(Petrophilepulchella.emmeans)
```

80. Plantago muelleri
```{r}
#getting sensitivity metric
Plantagomuellerimodel <- Sensitivitymodel(speciesselected = "Plantago muelleri") 
Plantagomuellerisensitivity <- Sensitivitymetric(model = Plantagomuellerimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Plantagomuellerimodel$coefficients, sigma = vcov(Plantagomuellerimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
PlantagomuelleriSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Plantagomuellerisensitivity) #save this number
print(PlantagomuelleriSE) #save this number
summary(Plantagomuellerimodel)
```

```{r}
Plantagomuelleri.emmeans <- emmeans(Plantagomuellerimodel, "Treatment")
pairs(Plantagomuelleri.emmeans)
```

81. Plectranthus parviflorus
```{r}
#getting sensitivity metric
Plectranthusparviflorusmodel <- Sensitivitymodel(speciesselected = "Plectranthus parviflorus") 
Plectranthusparviflorussensitivity <- Sensitivitymetric(model = Plectranthusparviflorusmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Plectranthusparviflorusmodel$coefficients, sigma = vcov(Plectranthusparviflorusmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
PlectranthusparviflorusSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Plectranthusparviflorussensitivity) #save this number
print(PlectranthusparviflorusSE) #save this number
summary(Plectranthusparviflorusmodel)
```

```{r}
Plectranthusparviflorus.emmeans <- emmeans(Plectranthusparviflorusmodel, "Treatment")
pairs(Plectranthusparviflorus.emmeans)
```

82. Plectranthus suaveolens
```{r}
#getting sensitivity metric
Plectranthussuaveolensmodel <- Sensitivitymodel(speciesselected = "Plectranthus suaveolens") 
Plectranthussuaveolenssensitivity <- Sensitivitymetric(model = Plectranthussuaveolensmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Plectranthussuaveolensmodel$coefficients, sigma = vcov(Plectranthussuaveolensmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
PlectranthussuaveolensSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Plectranthussuaveolenssensitivity) #save this number
print(PlectranthussuaveolensSE) #save this number
summary(Plectranthussuaveolensmodel)
```

```{r}
Plectranthussuaveolens.emmeans <- emmeans(Plectranthussuaveolensmodel, "Treatment")
pairs(Plectranthussuaveolens.emmeans)
```

83. Pomax umbellata
```{r}
#getting sensitivity metric
Pomaxumbellatamodel <- Sensitivitymodel(speciesselected = "Pomax umbellata") 
Pomaxumbellatasensitivity <- Sensitivitymetric(model = Pomaxumbellatamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Pomaxumbellatamodel$coefficients, sigma = vcov(Pomaxumbellatamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
PomaxumbellataSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Pomaxumbellatasensitivity) #save this number
print(PomaxumbellataSE) #save this number
summary(Pomaxumbellatamodel)
```

```{r}
Pomaxumbellata.emmeans <- emmeans(Pomaxumbellatamodel, "Treatment")
pairs(Pomaxumbellata.emmeans)
```

84. Rhodanthe anthemoides
```{r}
#getting sensitivity metric
Rhodantheanthemoidesmodel <- Sensitivitymodel(speciesselected = "Rhodanthe anthemoides") 
Rhodantheanthemoidessensitivity <- Sensitivitymetric(model = Rhodantheanthemoidesmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Rhodantheanthemoidesmodel$coefficients, sigma = vcov(Rhodantheanthemoidesmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
RhodantheanthemoidesSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Rhodantheanthemoidessensitivity) #save this number
print(RhodantheanthemoidesSE) #save this number
summary(Rhodantheanthemoidesmodel)
```

```{r}
Rhodantheanthemoides.emmeans <- emmeans(Rhodantheanthemoidesmodel, "Treatment")
pairs(Rhodantheanthemoides.emmeans)
```

85. Richea continentis
```{r}
#getting sensitivity metric
Richeacontinentismodel <- Sensitivitymodel(speciesselected = "Richea continentis") 
Richeacontinentissensitivity <- Sensitivitymetric(model = Richeacontinentismodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Richeacontinentismodel$coefficients, sigma = vcov(Richeacontinentismodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
RicheacontinentisSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Richeacontinentissensitivity) #save this number
print(RicheacontinentisSE) #save this number
```

86. Senecio linearifolius var. latifolius
```{r}
#getting sensitivity metric
Seneciolatifoliusmodel <- Sensitivitymodel(speciesselected = "Senecio linearifolius var. latifolius") 
Seneciolatifoliussensitivity <- Sensitivitymetric(model = Seneciolatifoliusmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Seneciolatifoliusmodel$coefficients, sigma = vcov(Seneciolatifoliusmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
SeneciolatifoliusSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Seneciolatifoliussensitivity) #save this number
print(SeneciolatifoliusSE) #save this number
summary(Seneciolatifoliusmodel)
```

```{r}
Seneciolatifolius.emmeans <- emmeans(Seneciolatifoliusmodel, "Treatment")
pairs(Seneciolatifolius.emmeans)
```

87. Senecio pinnatifolius subsp. alpinus
```{r}
#getting sensitivity metric
Senecioalpinusmodel <- Sensitivitymodel(speciesselected = "Senecio pinnatifolius subsp. alpinus") 
Senecioalpinussensitivity <- Sensitivitymetric(model = Senecioalpinusmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Senecioalpinusmodel$coefficients, sigma = vcov(Senecioalpinusmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
SenecioalpinusSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Senecioalpinussensitivity) #save this number
print(SenecioalpinusSE) #save this number
summary(Senecioalpinusmodel)
```

```{r}
Senecioalpinus.emmeans <- emmeans(Senecioalpinusmodel, "Treatment")
pairs(Senecioalpinus.emmeans)
```

88. Solanum aviculare 
```{r}
#getting sensitivity metric
Solanumavicularemodel <- Sensitivitymodel(speciesselected = "Solanum aviculare") 
Solanumavicularesensitivity <- Sensitivitymetric(model = Solanumavicularemodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Solanumavicularemodel$coefficients, sigma = vcov(Solanumavicularemodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
SolanumaviculareSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Solanumavicularesensitivity) #save this number
print(SolanumaviculareSE) #save this number
```

89. Syncarpia glomulifera
```{r}
#getting sensitivity metric
Syncarpiaglomuliferamodel <- Sensitivitymodel(speciesselected = "Syncarpia glomulifera") 
Syncarpiaglomuliferasensitivity <- Sensitivitymetric(model = Syncarpiaglomuliferamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Syncarpiaglomuliferamodel$coefficients, sigma = vcov(Syncarpiaglomuliferamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
SyncarpiaglomuliferaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Syncarpiaglomuliferasensitivity) #save this number
print(SyncarpiaglomuliferaSE) #save this number
summary(Syncarpiaglomuliferamodel)
```

```{r}
Syncarpiaglomulifera.emmeans <- emmeans(Syncarpiaglomuliferamodel, "Treatment")
pairs(Syncarpiaglomulifera.emmeans)
```

90. Symplocos wooroonooran
```{r}
#getting sensitivity metric
Symplocoswooroonooranmodel <- Sensitivitymodel(speciesselected = "Symplocos wooroonooran") 
Symplocoswooroonooransensitivity <- Sensitivitymetric(model = Symplocoswooroonooranmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Symplocoswooroonooranmodel$coefficients, sigma = vcov(Symplocoswooroonooranmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
SymplocoswooroonooranSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Symplocoswooroonooransensitivity) #save this number
print(SymplocoswooroonooranSE) #save this number
summary(Symplocoswooroonooranmodel)
```

```{r}
Symplocoswooroonooran.emmeans <- emmeans(Symplocoswooroonooranmodel, "Treatment")
pairs(Symplocoswooroonooran.emmeans)
```

91. Syzygium crebrinerve
```{r}
#getting sensitivity metric
Syzygiumcrebrinervemodel <- Sensitivitymodel(speciesselected = "Syzygium crebrinerve") 
Syzygiumcrebrinervesensitivity <- Sensitivitymetric(model = Syzygiumcrebrinervemodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Syzygiumcrebrinervemodel$coefficients, sigma = vcov(Syzygiumcrebrinervemodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
SyzygiumcrebrinerveSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Syzygiumcrebrinervesensitivity) #save this number
print(SyzygiumcrebrinerveSE) #save this number
```

92. Syzygium oleosum.B
#This species was collected from Border Ranges National Park
```{r}
#getting sensitivity metric
Syzygiumoleosum.Bmodel <- Sensitivitymodel(speciesselected = "Syzygium oleosum.B") 
Syzygiumoleosum.Bsensitivity <- Sensitivitymetric(model = Syzygiumoleosum.Bmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Syzygiumoleosum.Bmodel$coefficients, sigma = vcov(Syzygiumoleosum.Bmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Syzygiumoleosum.BSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Syzygiumoleosum.Bsensitivity) #save this number
print(Syzygiumoleosum.BSE) #save this number
```

93. Syzygium oleosum.Q
#This species was collected delivered from Wet Sclerophyll North Queensland
```{r}
#getting sensitivity metric
Syzygiumoleosum.Qmodel <- Sensitivitymodel(speciesselected = "Syzygium oleosum.Q") 
Syzygiumoleosum.Qsensitivity <- Sensitivitymetric(model = Syzygiumoleosum.Qmodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Syzygiumoleosum.Qmodel$coefficients, sigma = vcov(Syzygiumoleosum.Qmodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
Syzygiumoleosum.QSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Syzygiumoleosum.Qsensitivity) #save this number
print(Syzygiumoleosum.QSE) #save this number
summary(Syzygiumoleosum.Qmodel)
```

```{r}
Syzygiumoleosum.Q.emmeans <- emmeans(Syzygiumoleosum.Qmodel, "Treatment")
pairs(Syzygiumoleosum.Q.emmeans)
```

94. Syzygium australe
```{r}
#getting sensitivity metric
Syzygiumaustralemodel <- Sensitivitymodel(speciesselected = "Syzygium australe") 
Syzygiumaustralesensitivity <- Sensitivitymetric(model = Syzygiumaustralemodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Syzygiumaustralemodel$coefficients, sigma = vcov(Syzygiumaustralemodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
SyzygiumaustraleSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Syzygiumaustralesensitivity) #save this number
print(SyzygiumaustraleSE) #save this number
```

95. Tasmannia stipitata
```{r}
#getting sensitivity metric
Tasmanniastipitatamodel <- Sensitivitymodel(speciesselected = "Tasmannia stipitata") 
Tasmanniastipitatasensitivity <- Sensitivitymetric(model = Tasmanniastipitatamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Tasmanniastipitatamodel$coefficients, sigma = vcov(Tasmanniastipitatamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
TasmanniastipitataSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Tasmanniastipitatasensitivity) #save this number
print(TasmanniastipitataSE) #save this number
summary(Tasmanniastipitatamodel)
```

```{r}
Tasmanniastipitata.emmeans <- emmeans(Tasmanniastipitatamodel, "Treatment")
pairs(Tasmanniastipitata.emmeans)
```

96. Trachymene incisa
```{r}
#getting sensitivity metric
Trachymeneincisamodel <- Sensitivitymodel(speciesselected = "Trachymene incisa") 
Trachymeneincisasensitivity <- Sensitivitymetric(model = Trachymeneincisamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Trachymeneincisamodel$coefficients, sigma = vcov(Trachymeneincisamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
TrachymeneincisaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Trachymeneincisasensitivity) #save this number
print(TrachymeneincisaSE) #save this number
summary(Trachymeneincisamodel)
```

```{r}
Trachymeneincisa.emmeans <- emmeans(Trachymeneincisamodel, "Treatment")
pairs(Trachymeneincisa.emmeans)
```

97. Triunia erythrocarpa
```{r}
#getting sensitivity metric
Triuniaerythrocarpamodel <- Sensitivitymodel(speciesselected = "Triunia erythrocarpa") 
Triuniaerythrocarpasensitivity <- Sensitivitymetric(model = Triuniaerythrocarpamodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Triuniaerythrocarpamodel$coefficients, sigma = vcov(Triuniaerythrocarpamodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
TriuniaerythrocarpaSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Triuniaerythrocarpasensitivity) #save this number
print(TriuniaerythrocarpaSE) #save this number
summary(Triuniaerythrocarpamodel)
```

```{r}
Triuniaerythrocarpa.emmeans <- emmeans(Triuniaerythrocarpamodel, "Treatment")
pairs(Triuniaerythrocarpa.emmeans)
```

98. Vachellia bidwillii
```{r}
#getting sensitivity metric
Vachelliabidwilliimodel <- Sensitivitymodel(speciesselected = "Vachellia bidwillii") 
Vachelliabidwilliisensitivity <- Sensitivitymetric(model = Vachelliabidwilliimodel) 

#getting sensitivity SE
for(j in 1:10000){
  coeff_rep <- rmvnorm(1, mean = Vachelliabidwilliimodel$coefficients, sigma = vcov(Vachelliabidwilliimodel))
  Sensitivity_Metric_rep_parboot[j] <- sqrt(
    (coeff_rep[2]^2+coeff_rep[3]^2+(coeff_rep[3]-coeff_rep[2])^2)/3)
}
VachelliabidwilliiSE <- sd(Sensitivity_Metric_rep_parboot)

#printing the values so I can record them for the spreadsheet! :) 
print(Vachelliabidwilliisensitivity) #save this number
print(VachelliabidwilliiSE) #save this number
summary(Vachelliabidwilliimodel)
```


```{r}
Vachelliabidwillii.emmeans <- emmeans(Vachelliabidwilliimodel, "Treatment")
pairs(Vachelliabidwillii.emmeans)
```

#End of code







