---
title: "Dataset_Processing"
output: html_notebook
---
#load in packages and data
```{r}
library(tidyverse)
library(data.table) #recommended package for reading raw TRY data

library(sp) #the older spatial package
library(sf) #the newer, simpler spatial package

library(ncdf4) #for reading/manipulating Copernicus data

library(raster) #for general raster data

```


```{r}
df <- read.csv("./data/appendix1.csv")
df <- df %>% filter(df$source_located == "yes")
```

#Fill in coordinates
```{r}
#convert na to zero
df$lat_d[is.na(df$lat_d)] <- 0
df$lat_m[is.na(df$lat_m)] <- 0
df$lat_s[is.na(df$lat_s)] <- 0

df$lon_d[is.na(df$lon_d)] <- 0
df$lon_m[is.na(df$lon_m)] <- 0
df$lon_s[is.na(df$lon_s)] <- 0

#create new row of decimal from dms coordinates

df$temp_replace_lat <- (df$lat_d + (df$lat_m)/60 + (df$lat_s)/360)
df$temp_replace_lon <- (df$lon_d + (df$lon_m)/60 + (df$lon_s)/360)

#when there are no decimal coordinates, replace with converted dms coordinates

df$lat_decimaldegree[is.na(df$lat_decimaldegree)] <- df$temp_replace_lat[is.na(df$lat_decimaldegree)]

df$lon_decimaldegree[is.na(df$lon_decimaldegree)] <- df$temp_replace_lon[is.na(df$lon_decimaldegree)]

#convert S and E to negative coordinates

df$lat_decimaldegree[df$lat_NS == "s"] <- df$lat_decimaldegree[df$lat_NS == "s"]*-1

df$lon_decimaldegree[df$lon_EW == "w"] <- df$lon_decimaldegree[df$lon_EW == "w"]*-1

```

#Seed Mass

Checking the TRY Database: 

Kattge, J, Boenisch, G, Diaz, S, et al. TRY plant trait database - enhanced coverage and open access. Glob Change Biol. 2020; 26: 119-188. https://doi.org/10.1111/gcb.14904

```{r}
try <- fread("./data/raw/15636_TRY/15636.txt")
 
unique(try$AccSpeciesName) # we just want the seed masses per species

try <- try %>% filter(OriglName == "estimated total seed mass")

```
This isn't good, we only have 9 species...

Let's check kew first and come back to it.

Checking the Kew Gardens records.
I manually ctrl-f searched my way through our records since I couldn't find a data portal option.

(Royal Botanic Gardens Kew. (2021) Seed Information Database (SID). Version 7.1. Available from: http://data.kew.org/sid/ (July 2021)) 

TO DO: I also applied a correction based on dry vs wet weight of seeds according to [citation]


```{r}
df <- read.csv( "./data/kew_check.csv")

table(is.na(df$seed_mass))
```
Much better, 109 seed mass records!

Now back to TRY to try get more records

```{r}
df$species[is.na(df$seed_mass) == T] 

unique(try$AccSpeciesName) %in% #compare list of species seed weights available in try
  df$species[is.na(df$seed_mass) == T] # with list species that are missing
```
And they don't overlap, that's ok. we TRY our best.

```{r}
rm(try)
```

#Alpine (unused, see end of section for context)

Alpine shapefile obtained from: Testolin, Riccardo; Attorre, Fabio; Jiménez-Alfaro, Borja (2020): Global distribution and bioclimatic characterization of alpine biomes. figshare. Dataset. https://doi.org/10.6084/m9.figshare.11710002.v1  

Note that google uses EPSG:3857 while normal  WGS84 is EPSG:4326.
The transformation between google and normal caused worse issues than untransformed (maybe since the google one is ill defined?), and they are around the same anyways so I decided to assume they are the same. Sorry. 
```{r}

df$coordinates <- df[,5:6] %>%  #Turn latitude and longitude into coordinates
  as.data.frame %>% 
  st_as_sf(coords = c(2,1)) %>%
  st_set_crs("EPSG:4326")


plot(df$coordinates)

```

#clean up alpine polygons
(v slow)
```{r}
alpine <- st_read(dsn = "./data/alpine_clusters", layer = "alpine_clusters")


any(is.na(st_dimension(alpine)))#at least there are no empty geometries, 
any(is.na(st_is_valid(alpine))) #or corrupt geometries
any(na.omit(st_is_valid(alpine)) == FALSE) #but there are invalid ones

#table(st_is_valid(alpine, reason = T)) #for a single polygon, edge 0 crosses edge 3 in 

st_intersects(df$coordinates[1, ], alpine, sparse = F) #the problem is in object 36955
alpine$ecoregion[36955] # in the "Hengduan Mountains Subalpine Conifer Forests"

alpine <- st_make_valid(alpine) %>% st_cast("MULTIPOLYGON") #make the loops valid, this takes a long time

st_intersects(df$coordinates[1, ], alpine, sparse = F) #there is still a problem

plot(alpine$geometry[36955]) #the shape intersects itself

alpine$geometry[[36955]][[1]][[1]] #look at the individual points

#if we move point 4 sliiiightly down by 0.1 degree, there will no longer be an overlap
#and it will be fixed

alpine$geometry[[36955]][[1]][[1]][[4,2]] <- 32.20227

table(st_is_valid(alpine, reason = T)) #everything is valid!

plot(alpine) #plot
```

#Check for intersection between alpine zones and our coordinates
```{r}
intersection <- st_intersects(df$coordinates, alpine$geometry, sparse = FALSE) #very slow

alpine_records <- which(intersection, arr.ind = T) #which row (df row) and column (alpine polygon) is intersecting?

alpine_records

df[67 ,] #have a look at what the intersecting alpine regions and the records were
alpine$ecoregion[[29318]]
df[50 ,]
alpine$ecoregion[[38661]]
df[68 ,]
alpine$ecoregion[[46203]]

df$alpine <- "0"
df$alpine[67] <- "1"  #Add info to df
df$alpine[50] <- "1" 
df$alpine[68] <- "1"

rm(alpine, intersection)#remove the extra info
```
Just out of interest, I pulled the ecoregions of the alpine points.

50: Mt Slattajaka
in the "Scandinavian Montane Birch Forest And Grasslands"

67:Col du Lautaret, Hautes Alps de Provence, France
in the "Alps Conifer And Mixed Forests"

68: Finse, Hardangervidda, Ulvik, Norway
in the "Scandinavian Montane Birch Forest And Grasslands"
Very cool.


This is very few points. 

Some locations known to be alpine were also not detected, and alpine status of source populations were difficult to resolve. 

Eg. Some mimulus guttatas populations identified as alpine populations in original source existed below treeline, but also could extend above treeline. 

Because of difficulties in determining whether a source could be considered an alpine population, we decided it was best to put aside this analysis.

```{r}
# df <- read.csv("./data/alpine_check.csv") #Unused option for a manual check of alpine records
```

#LAI

We obtained NDVI from copernicus.

```{r}
nc <- nc_open("./data/copernicus_ndvi_1km_5y/c_gls_NDVI-STS_2015-2019-0611_GLOBE_PROBAV_V3.0.1.nc")

names(nc$var) #names of the variables to choose from

ndvi_raster<- raster("./data/copernicus_ndvi_1km_5y/c_gls_NDVI-STS_2015-2019-0611_GLOBE_PROBAV_V3.0.1.nc", varname = "median") #choose the median

```

Since most of the plants on the list seem to be herbaceous grassland species, I have decided to use a conversion equation made using grassland data: Fan, L., Gao, Y., Brück, H. et al. Investigating the relationship between NDVI and LAI in semi-arid grassland in Inner Mongolia using in-situ measurements. Theor Appl Climatol 95, 151–156 (2009). https://doi.org/10.1007/s00704-007-0369-2
LAI = 0.128 * exp(NDVI/0.311)
```{r}
df$NDVI <- raster::extract(ndvi_raster, df$coordinates, method = "simple")
df$LAI <- 0.128 * exp(df$NDVI/0.311)
```

#Create minimum temperature raster from worldclim (unused in paper)

Fick, S.E. and R.J. Hijmans, 2017. WorldClim 2: new 1km spatial resolution climate surfaces for global land areas. International Journal of Climatology 37 (12): 4302-4315.

```{r}
mintemp_raster_1 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_01.tif")
mintemp_raster_2 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_02.tif")
mintemp_raster_3 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_03.tif")
mintemp_raster_4 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_04.tif")
mintemp_raster_5 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_05.tif")
mintemp_raster_6 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_06.tif")
mintemp_raster_7 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_07.tif")
mintemp_raster_8 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_08.tif")
mintemp_raster_9 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_09.tif")
mintemp_raster_10 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_10.tif")
mintemp_raster_11 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_11.tif")
mintemp_raster_12 <- raster("./data/wc2.1_10m_tmin/wc2.1_10m_tmin_12.tif")


mintemp_raster_all <- overlay(mintemp_raster_1, mintemp_raster_2, mintemp_raster_3, mintemp_raster_4, mintemp_raster_5, mintemp_raster_6, mintemp_raster_7, mintemp_raster_8, mintemp_raster_9, mintemp_raster_10, mintemp_raster_11, mintemp_raster_12, fun = min)

plot(mintemp_raster_all)
```
#find minimum temperature for all coordinates
```{r}
df$temp_min <- raster::extract(mintemp_raster_all, df$coordinates, method = "simple")
```

#create a clean final dataset from df
```{r}
df_output <- transmute(df, species = species, photoperiodism = photoperiodism, source_name = source_name, lat = lat_decimaldegree, lon = lon_decimaldegree, year = year, LAI = LAI, min_temp = temp_min, seed_mass = seed_mass, alpine = alpine, elevation = elevation, cultivar = cultivar, reference = reference, notes = notes)

write.csv(df_output, "./output/photoperiod_global_addition.csv", row.names = FALSE)
```

#clear up environment
```{r}
rm(mintemp_raster_1, mintemp_raster_2, mintemp_raster_3, mintemp_raster_4, mintemp_raster_5, mintemp_raster_6, mintemp_raster_7, mintemp_raster_8, mintemp_raster_9, mintemp_raster_10, mintemp_raster_11, mintemp_raster_12, nc, ndvi_raster, alpine_records, mintemp_raster_all)
```

## Match family using rGBIF
```{r}
library(rgbif)
```

Check environment (you will need a freely available GBIF login to run)
```{r}
usethis::edit_r_environ() #edit environment to include gbif login details in a way that saves it locally on the computer running the code (you don't get my login details sorry)
```

round latlon
```{r}
df_output$lat <- round(df_output$lat, digits = 2)
df_output$lon <- round(df_output$lon, digits = 2)
```


Fix up reading errors
```{r}
df_output$species <- gsub(pattern = "<a0>", replacement = " ", df_output$species)
```

Check for matching taxon in GBIF to obtain family, print out to check that the families make sense
```{r}
gbif_taxon_check <- name_backbone_checklist(df_output$species)

gbif_taxon_check
```
Append family info onto output and save over previous csv
```{r}
df_output$family <- gbif_taxon_check$family
write.csv(df_output, "./output/photoperiod_global_addition.csv", row.names = FALSE)
```

