---
title: "Main Analysis"
author: "Ashika Jagdish"
date: "29/08/2020"
output:
  html_document: default
  pdf_document: default
---

Main Analyses for Jagdish et al. (In Review) - Shining a light on patterns of photoperiod sensitivty in seed germination across latitudes, ecosystems and functional traits

- see Rmarkdown "BayesianPhotoperiodMetricOfficial.Rmd" for gaining a photoperiod sensitivity index for each species using bayesian GLMs
- see Rmarkdown file "PhylogeneticAnalysis.Rmd" for Phylogenetic Analyses of photoperiod sensitivity across our species
- see Rmarkdown "Analysis of flowering photoperiod and predictor variables" for a similar analysis to this current script except instead of germination photoperiod the categorical response variable flowering photoperiod sensitivity - (long day, short day or non-sensitive to photoperiod) logistically regressed against against environmental/ecological predictor variables

This code is a multiple part series, each hypothesis (photoperiod related to each variable) is one part


Step 1: Call all relevant libraries
```{r}
library(lme4)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(rcompanion)
library(emmeans)
library(rstatix)
library(ggpubr)
library(Hmisc)
library(glmmTMB)
library(fuzzyjoin)
library(parameters)
```

Step 2: Read in data 

```{r}
LessThan5 <- read.csv("LessThan5.csv") #LessThan5.csv - Species which had <5% germination in all treatments or <5 seeds germinated across all 3 treatments were removed from further analyses
```

```{r}
LessThan5LDSD <- read.csv("LessThan5LDSD.csv") # LessThan5LDSD.csv - Species which had <5% germination in all treatments or <5 seeds germinated across all 3 treatments were removed from further analyses, where species were weighted as being short-day sensitive, long-day sensitive, based off raw germination results. Species which were neither long-day sensitive, nor short-day sensitive, were half-weighted as short-day, and half-weighted as long-day.
```

```{r}
RawBinaryGermData <- read.csv("RawBinaryGermData.csv")#also reading in raw data because we will run supplementary analysis with bayesian models of the germination data

RawGerminationData <- RawBinaryGermData %>%
  filter(!Species == "Cissus hypoglauca.B" & !Species == "Cissus hypoglauca.M" & !Species == "Syzygium oleosum.B" & !Species == "Linospadix monostachya.D") %>%
  stringdist_left_join(., LessThan5, by = "Species", max_dist = 2) %>%
  filter(!is.na(Species.y)) #creating a data frame in all these lines that ONLY has species that we run the main analyses for
```

Step 3: Distribution of the data
Our data is gamma distributed, log transforming the data does not make it look better visually
```{r}
hist(LessThan5$PP.Sensitivity)
```

```{r}
hist(LessThan5LDSD$PP.Sensitivity.Sign)
```

Step 4: Running the models

PART 1:

#PHOTOPERIOD SENSITIVITY AND LATITUDE

A) I) The 'Original' model (prior to classifying species as long-day sensitive, short-day sensitive, or neither (contributes half to both): 
```{r}
latitudemodel <- glm(PP.Sensitivity~Latitude, family = Gamma(link = "identity"), data =LessThan5, weights = 1/(SE^2))

summary(latitudemodel)
plot(latitudemodel)
```

A. II) Model comparing latitude and LD/SD:
```{r}
latitudemodelLDSD <- glm(PP.Sensitivity~PP.Sensitivity.Sign + Latitude + PP.Sensitivity.Sign * Latitude, family = gaussian(link = "identity"), data =LessThan5LDSD, weights = Weight)

summary(latitudemodelLDSD)
plot(latitudemodelLDSD)
```

B) I) Plot of 'Original':
```{r}
latitudeplot <- ggplot(aes(x=Latitude, y=(PP.Sensitivity)), data=LessThan5) +
  geom_point(color = "lightsalmon2", size = 4, alpha = 0.8) + theme_classic() + labs(x = "Latitude (°S)", y = "Photoperiod Sensitivity Index") + theme(
  axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(latitudeplot)

ggsave(latitudeplot, 
       filename = "latitudeplot.jpg",
       width = 7,
       height = 7,
       dpi=600)
```

#Nagelkerke Pseudo R^2 values for the 'Original' model 
```{r}
nagelkerke(latitudemodel)
```

#Nagelkerke Pseudo R^2 values for the LD/SD model:
```{r}
nagelkerke(latitudemodelLDSD)
```

#model as a bayesian metric with raw data for supplement
```{r}
#run model
glmlatitudefit <- glmmTMB(No.Germinated ~ scale(Latitude)+Treatment+scale(Latitude):Treatment + (1+Treatment|Species.x), data = RawGerminationData, family = "binomial")
summary(glmlatitudefit)

#test for singularity 
ranef(glmlatitudefit) #no very low values - no singularity

#calculate slope
slopelatitude = sqrt((fixef(glmlatitudefit)[[1]]["scale(Latitude):TreatmentLong"]^2 + fixef(glmlatitudefit)[[1]]["scale(Latitude):TreatmentShort"]^2 + (fixef(glmlatitudefit)[[1]]["scale(Latitude):TreatmentLong"] - fixef(glmlatitudefit)[[1]]["scale(Latitude):TreatmentLong"])^2 )/3)

slopelatitude # 0.074

# calculate standard error of the slope

simulatelatitude = simulate_model(glmlatitudefit, iterations = 100, verbose = TRUE)


slope_reps_latitude = sqrt((simulatelatitude[,"scale(Latitude):TreatmentLong"]^2 + simulatelatitude[,"scale(Latitude):TreatmentShort"]^2 + (simulatelatitude["scale(Latitude):TreatmentLong"] - simulatelatitude[,"scale(Latitude):TreatmentLong"])^2) /3)

#summarise slope and SE for appendix
summary_one_step_latitude = c(slopelatitude, SE_slope = sd(slope_reps_latitude[,1]))

summary_one_step_latitude
```



PART 2:

#PHOTOPERIOD SENSITIVITY AND SEED MASS

A) I) The 'Original' seed mass model:
```{r}
seedmassmodel <- glm(PP.Sensitivity~Seed.Mass.Mg, family = Gamma(link = "identity"), start = c(0.5, 0.5), data = LessThan5, weights = 1/(SE^2))

summary(seedmassmodel)
plot(seedmassmodel)
```

A) II) The 'Original' seed mass model log10 transformed x-axis:
```{r}
seedmassplot <- ggplot(aes(x=(Seed.Mass.Mg), y=(PP.Sensitivity)), data=LessThan5) +
  geom_point(color = "lightsalmon2", size =4, alpha = 0.8) + theme_classic() + scale_x_continuous(trans='log10') + xlab(expression(Seed~Mass~(mg)~(Log["10"]~Scale))) + labs(y = "Photoperiod Sensitivity Index") + theme(
  axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(seedmassplot)

ggsave(seedmassplot, 
       filename = "seedmassplot.jpg",
       width = 7,
       height = 7,
       dpi=600)
```

B. I) Seed Mass and LD/SD:
```{r}
seedmassmodelLDSD <- glm(PP.Sensitivity~PP.Sensitivity.Sign + Seed.Mass.Mg + PP.Sensitivity.Sign * Seed.Mass.Mg, family = gaussian(link = "identity"), data =LessThan5LDSD, weights = Weight)

summary(seedmassmodelLDSD)
plot(seedmassmodelLDSD)
```

#Nagelkerke Pseudo-R^2 value for 'Original':
```{r}
seedmassmodel_null <- glm(PP.Sensitivity~1, family = Gamma(link = "identity"), data = LessThan5, weights = 1/(SE^2))

summary(seedmassmodel_null)
plot(seedmassmodel_null)

nagelkerke (seedmassmodel, seedmassmodel_null)
```

#Nagelkerke Pseudo-R^2 value for Seed Mass and LD/SD:
```{r}
nagelkerke (seedmassmodelLDSD)
```


#model as a bayesian metric with raw data for supplement
```{r}
#run model
glmseedmassfit <- glmmTMB(No.Germinated ~ scale(Seed.Mass.Mg)+Treatment+scale(Seed.Mass.Mg):Treatment + (1+Treatment|Species.x), data = RawGerminationData, family = "binomial")
summary(glmseedmassfit)

#test for singularity 
ranef(glmseedmassfit) #not too many very low values - no singularity

#calculate slope
slopeseedmass = sqrt((fixef(glmseedmassfit)[[1]]["scale(Seed.Mass.Mg):TreatmentLong"]^2 + fixef(glmseedmassfit)[[1]]["scale(Seed.Mass.Mg):TreatmentShort"]^2 + (fixef(glmseedmassfit)[[1]]["scale(Seed.Mass.Mg):TreatmentLong"] - fixef(glmseedmassfit)[[1]]["scale(Seed.Mass.Mg):TreatmentLong"])^2 )/3)

slopeseedmass # 0.091

# calculate standard error of the slope

simulateseedmass = simulate_model(glmseedmassfit, iterations = 100, verbose = TRUE)

slope_reps_seedmass = sqrt((simulateseedmass[,"scale(Seed.Mass.Mg):TreatmentLong"]^2 + simulateseedmass[,"scale(Seed.Mass.Mg):TreatmentShort"]^2 + (simulateseedmass["scale(Seed.Mass.Mg):TreatmentLong"] - simulateseedmass[,"scale(Seed.Mass.Mg):TreatmentLong"])^2) /3)

#summarise slope and SE for appendix
summary_one_step_seedmass = c(slopeseedmass, SE_slope = sd(slope_reps_seedmass[,1]))

summary_one_step_seedmass
```


PART 3:

#PHOTOPERIOD SENSITIVITY AND LEAF AREA INDEX (LAI)

A) I) The 'Original' model: 
```{r}
LAImodel <- glm(PP.Sensitivity~LAI, family = Gamma(link = "identity"), start = c(0.5, 0.5), data =LessThan5, weights = 1/(SE^2))

summary(LAImodel)
plot(LAImodel)
```

A. II) 'Original' Plot
```{r}
LAIplot <- ggplot(aes(x=LAI, y=PP.Sensitivity), data=LessThan5) +
  geom_point(color = "lightsalmon2", size=4, alpha = 0.8) + theme_classic() +  xlab(expression(Leaf~Area~Index~(m^{"2"}~m^-2))) +  labs(y = "Photoperiod Sensitivity Index") + theme(
  axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(LAIplot)

ggsave(LAIplot, 
       filename = "LAIplot.jpg",
       width = 7,
       height = 7,
       dpi=600)
```

B) I) LAI AND LD/SD:
```{r}
laimodelLDSD <- glm(PP.Sensitivity~PP.Sensitivity.Sign + LAI + PP.Sensitivity.Sign * LAI, family = gaussian(link = "identity"), data =LessThan5LDSD, weights = Weight)

summary(laimodelLDSD)
plot(laimodelLDSD)
```

#Nagelkerke Pseudo R^2 for LAI 'Original':
```{r}
LAImodel_null <- glm(PP.Sensitivity~1, family = Gamma(link = "identity"), data =LessThan5, weights = 1/(SE^2))

summary(LAImodel_null)
plot(LAImodel_null)

nagelkerke (LAImodel, LAImodel_null)
```

#Nagelkerke for LAI LD/SD:
```{r}
nagelkerke (laimodelLDSD)
```

#model as a bayesian metric with raw data for supplement
```{r}
#run model
glmLAIfit <- glmmTMB(No.Germinated ~ scale(LAI)+Treatment+scale(LAI):Treatment + (1+Treatment|Species.x), data = RawGerminationData, family = "binomial")
summary(glmLAIfit)

#test for singularity 
ranef(glmLAIfit) #not low values - no singularity

#calculate slope
slopeLAI = sqrt((fixef(glmLAIfit)[[1]]["scale(LAI):TreatmentLong"]^2 + fixef(glmLAIfit)[[1]]["scale(LAI):TreatmentShort"]^2 + (fixef(glmLAIfit)[[1]]["scale(LAI):TreatmentLong"] - fixef(glmLAIfit)[[1]]["scale(LAI):TreatmentLong"])^2 )/3)

slopeLAI # 0.239

# calculate standard error of the slope

simulateLAI = simulate_model(glmLAIfit, iterations = 100, verbose = TRUE)

slope_reps_LAI = sqrt((simulateLAI[,"scale(LAI):TreatmentLong"]^2 + simulateLAI[,"scale(LAI):TreatmentShort"]^2 + (simulateLAI["scale(LAI):TreatmentLong"] - simulateLAI[,"scale(LAI):TreatmentLong"])^2) /3)

#summarise slope and SE for appendix
summary_one_step_LAI = c(slopeLAI, SE_slope = sd(slope_reps_LAI[,1]))

summary_one_step_LAI
```

PART 4:

#PHOTOPERIOD SENSITIVITY AND ALPINE VS. NON-ALPINE HABITATS

A) I) The 'Original' model: 
```{r}
alpmodel <- glm(PP.Sensitivity~Alpine.Habitat, family = Gamma(link = "identity"), data =LessThan5, weights = 1/(SE^2))

summary(alpmodel)
plot(alpmodel)
```

A) II) The 'Original' Plot:
```{r}
alpplot <- LessThan5 %>% ggplot(aes(x=Alpine.Habitat, y=PP.Sensitivity)) + 
  geom_violin(width=0.5,lwd=0.5, fill="skyblue", alpha = 0.8) + stat_summary(fun.data='mean_sd', color='black') + theme_classic() + labs(x = "Ecosystem Type", y = "Photoperiod Sensitivity Index") + theme(
  axis.text=element_text(size=16),
        axis.title=element_text(size=20))

plot(alpplot)

ggsave(alpplot,
       filename = "alpplot.jpg",
       width=7,
       height=7,
       dpi=600)
```

B) I) The LD/SD model: 
```{r}
alpmodelLDSD <- glm(PP.Sensitivity~PP.Sensitivity.Sign + Alpine.Habitat + PP.Sensitivity.Sign * Alpine.Habitat, family = gaussian(link = "identity"), data =LessThan5LDSD, weights = Weight)

summary(alpmodelLDSD)
plot(alpmodelLDSD)
```


#Nagelkerke Pseudo R^2 Value for 'Original' model:
```{r}
nagelkerke(alpmodel)
```

#Nagelkerke Pseudo R^2 Value for LD/SD model:
```{r}
nagelkerke(alpmodelLDSD)
```

#model as a bayesian metric with raw data for supplement
````{r}
#because alpine vs. non-alpine growth forms are a factor predictor variable - the code is slightly different to the continuous predictor variables previously (latitiude, seed mass, LAI)
#run model
glmalpinefit <- glmmTMB(No.Germinated ~ Alpine.Habitat+Treatment+Alpine.Habitat:Treatment + (1+Treatment|Species.x), data = RawGerminationData, family = "binomial")
summary(glmalpinefit)

#test for singularity 
ranef(glmalpinefit) #not low values - no singularity

#Extract the coefficient data (this has added in the random effects)
coef_alpine = coef(glmalpinefit)[[1]]$Species %>% 
  mutate(Species.x = rownames(.)) #adding a column for species

# for each level of the factor variable (2 levels - alpine or non-alpine), calculate the PPS separately

#Level 1 is the reference level (Alpine)
coef_data_nonalpine = 
  coef_alpine %>% 
  left_join(RawGerminationData [, c("Alpine.Habitat","Species.x")]) %>%
  subset(Alpine.Habitat == "Alpine") %>%
  mutate(Treat2_effect_per_species = `TreatmentLong`) %>%
  mutate(Treat3_effect_per_species = `TreatmentShort`) %>% 
  mutate(PPS = sqrt((Treat2_effect_per_species^2 +Treat3_effect_per_species^2 +(Treat2_effect_per_species-Treat3_effect_per_species)^2)/3))


#Level 2 
coef_data_alpine = 
  coef_alpine %>% 
  left_join(RawGerminationData [, c("Alpine.Habitat","Species.x")]) %>%
  subset(Alpine.Habitat == "Non-Alpine") %>%
  mutate(Treat2_effect_per_species = `Alpine.HabitatNon-Alpine:TreatmentLong` + `TreatmentLong`) %>%
  mutate(Treat3_effect_per_species = `Alpine.HabitatNon-Alpine:TreatmentShort` + `TreatmentLong`) %>% 
  mutate(PPS = sqrt((Treat2_effect_per_species^2 +Treat3_effect_per_species^2 +(Treat2_effect_per_species-Treat3_effect_per_species)^2)/3))


PPS_vs_alpine_Data = bind_rows(coef_data_alpine,coef_data_nonalpine)

ggplot(PPS_vs_alpine_Data, aes(Alpine.Habitat, PPS)) + geom_violin()


#for a factor there is no slope, only mean differences. 
#Photo period sensitivity change  difference between Level 2 and 1. 
slope_level1_2 = sqrt((fixef(glmalpinefit)[[1]]["Alpine.HabitatNon-Alpine:TreatmentLong"]^2 + fixef(glmalpinefit)[[1]]["Alpine.HabitatNon-Alpine:TreatmentShort"]^2 + (fixef(glmalpinefit)[[1]]["Alpine.HabitatNon-Alpine:TreatmentLong"])^2 )/3)


names(slope_level1_2 ) = "mean diff (L2-L1)"
slope_level1_2 

#To calculate the SE of the slope 

simulate_alpine = simulate_model(glmalpinefit, iterations = 100, verbose = TRUE)


# SE of mean PPS level 2 - level 1. 
slope_reps_level1_2 = sqrt((simulate_alpine[,"Alpine.HabitatNon-Alpine:TreatmentLong"]^2 + simulate_alpine[,"Alpine.HabitatNon-Alpine:TreatmentShort"]^2 + (simulate_alpine["Alpine.HabitatNon-Alpine:TreatmentLong"] - simulate_alpine[,"Alpine.HabitatNon-Alpine:TreatmentLong"])^2) /3)

summary_one_step_level1_2 = c(slope_level1_2, SE_slope = sd(slope_reps_level1_2[,1]))

summary_one_step_level1_2
```

PART 5:

#PHOTOPERIOD SENSITIVITY AND GROWTH FORM


```{r}
LessThan5GF <- read.csv("LessThan5GF.csv") #Reading in .csv file with species growth-form which excludes the climbers species (n=2)
hist(LessThan5GF$PP.Sensitivity) #visualisation plot
```

```{r}
LessThan5GFLDSD <- read.csv("LessThan5GFLDSD.csv") #LessThan5GFLDSD.csv is where species have been categorised as long-day sensitive, short-day sensitive etc.
hist(LessThan5GFLDSD$PP.Sensitivity.Sign) #visualisation plot
```

A) I) The 'Original' model:
#Setting Growth Form as a factor:
```{r}
str(LessThan5GF$Growth.Form)
LessThan5GF$Growth.Form <- as.factor(LessThan5GF$Growth.Form)
```

```{r}
gfmodel <- glm(PP.Sensitivity~Growth.Form, family = Gamma(link = "identity"), data =LessThan5GF, weights = 1/(SE^2))

summary(gfmodel) #gives between group results
drop1(gfmodel, test = "F") #result of growth form overall
```

A) II) The 'Original' Plot:
```{r}
GFplot <- LessThan5GF %>% ggplot(aes(x=Growth.Form, y=PP.Sensitivity)) + 
  geom_violin(width=0.5,lwd=0.5, fill="skyblue", alpha=0.8) + stat_summary(fun.data='mean_sd', color='black') + theme_classic() + labs(x = "Growth Form", y = "Photoperiod Sensitivity Index") + theme(
  axis.text=element_text(size=16),
        axis.title=element_text(size=20))
plot(GFplot)

ggsave(GFplot,
       filename= "GFplot.jpg",
       width=7,
       height=7,
       dpi=600)
```

B) I) The LD/SD model: 
#Setting Growth Form as a factor:
```{r}
str(LessThan5GFLDSD$Growth.Form)
LessThan5GFLDSD$Growth.Form <- as.factor(LessThan5GFLDSD$Growth.Form)
```

```{r}
gfmodelLDSD <- glm(PP.Sensitivity~PP.Sensitivity.Sign + Growth.Form + PP.Sensitivity.Sign * Growth.Form, family = gaussian(link = "identity"), data =LessThan5GFLDSD, weights = Weight)

summary(gfmodelLDSD)
plot(gfmodelLDSD)
``` 

#Nagelkere PseUdo R^2 Value for 'Original':
```{r}
nagelkerke(gfmodel)
```

#Nagelkere PseUdo R^2 Value for LD/SD:
```{r}
nagelkerke(gfmodelLDSD)
```

#model as a bayesian metric with raw data for supplement
````{r}
#because growth forms are a factor predictor variable - the code is slightly different to the continuous predictor variables previously (latitiude, seed mass, LAI)

#for this analysis we also need to first take the climbing plants out - we didn't analyse them in the main analyses above because there are only two species with this growth form

RawGerminationDataGrowthForm <- RawGerminationData %>%
  filter(!Growth.Form == "Climber")

#run model
glmgrowthformfit <- glmmTMB(No.Germinated ~ Growth.Form +Treatment+Growth.Form:Treatment + (1+Treatment|Species.x), data = RawGerminationDataGrowthForm, family = "binomial")
summary(glmgrowthformfit)

#test for singularity 
ranef(glmgrowthformfit) #not low values - no singularity

#Extract the coefficient data (this has added in the random effects)
coef_growthform = coef(glmgrowthformfit)[[1]]$Species %>% 
  mutate(Species.x = rownames(.)) #adding a column for species

# for each level of the factor variable (3 levels - herb, shrub, tree), calculate the PPS separately

#Level 1 is the reference level (Herb)
coef_data_herb = 
  coef_growthform %>% 
  left_join(RawGerminationDataGrowthForm [, c("Growth.Form","Species.x")]) %>%
  subset(Growth.Form == "Herb") %>%
  mutate(Treat2_effect_per_species = `TreatmentLong`) %>%
  mutate(Treat3_effect_per_species = `TreatmentShort`) %>% 
  mutate(PPS = sqrt((Treat2_effect_per_species^2 +Treat3_effect_per_species^2 +(Treat2_effect_per_species-Treat3_effect_per_species)^2)/3))


#Level 2(Shrub)
coef_data_shrub = 
  coef_growthform %>% 
  left_join(RawGerminationDataGrowthForm [, c("Growth.Form","Species.x")]) %>%
  subset(Growth.Form == "Shrub") %>%
  mutate(Treat2_effect_per_species = `TreatmentLong`) %>%
  mutate(Treat3_effect_per_species = `TreatmentShort`) %>% 
  mutate(PPS = sqrt((Treat2_effect_per_species^2 +Treat3_effect_per_species^2 +(Treat2_effect_per_species-Treat3_effect_per_species)^2)/3))

#Level 3 (Tree)
coef_data_tree = 
  coef_growthform %>% 
  left_join(RawGerminationDataGrowthForm [, c("Growth.Form","Species.x")]) %>%
  subset(Growth.Form == "Tree") %>%
  mutate(Treat2_effect_per_species = `TreatmentLong`) %>%
  mutate(Treat3_effect_per_species = `TreatmentShort`) %>% 
  mutate(PPS = sqrt((Treat2_effect_per_species^2 +Treat3_effect_per_species^2 +(Treat2_effect_per_species-Treat3_effect_per_species)^2)/3))


PPS_vs_growthform_Data = bind_rows(coef_data_herb,coef_data_shrub,coef_data_tree)

ggplot(PPS_vs_growthform_Data, aes(Growth.Form, PPS)) + geom_violin()


#for a factor there is no slope, only mean differences. 
#Photo period sensitivity change  difference between Level 2 and 1. 
slope_level1_2 = sqrt((fixef(glmgrowthformfit)[[1]]["Growth.FormShrub:TreatmentLong"]^2 + fixef(glmgrowthformfit)[[1]]["Growth.FormShrub:TreatmentShort"]^2 + (fixef(glmgrowthformfit)[[1]]["Growth.FormShrub:TreatmentLong"] - fixef(glmgrowthformfit)[[1]]["Growth.FormShrub:TreatmentLong"])^2 )/3)

slope_level1_2

#Photo period sensitivity change  difference between Level 3 and 1. 
slope_level1_3 = sqrt((fixef(glmgrowthformfit)[[1]]["Growth.FormTree:TreatmentLong"]^2 + fixef(glmgrowthformfit)[[1]]["Growth.FormTree:TreatmentShort"]^2 + (fixef(glmgrowthformfit)[[1]]["Growth.FormTree:TreatmentLong"] - fixef(glmgrowthformfit)[[1]]["Growth.FormTree:TreatmentLong"])^2 )/3)

slope_level1_3


#To calculate the SE of the slope 

simulate_growthform = simulate_model(glmgrowthformfit, iterations = 100, verbose = TRUE)


# SE of mean PPS level 2 - level 1. 
slope_reps_level1_2 = sqrt((simulate_growthform[,"Growth.FormShrub:TreatmentLong"]^2 + simulate_growthform[,"Growth.FormShrub:TreatmentLong"]^2 + (simulate_growthform["Growth.FormShrub:TreatmentShort"] - simulate_growthform[,"Growth.FormShrub:TreatmentLong"])^2) /3)

summary_one_step_level1_2 = c(slope_level1_2, SE_slope = sd(slope_reps_level1_2[,1]))

summary_one_step_level1_2

# SE of mean PPS level 3 - level 1. 
slope_reps_level1_3 = sqrt((simulate_growthform[,"Growth.FormTree:TreatmentLong"]^2 + simulate_growthform[,"Growth.FormTree:TreatmentLong"]^2 + (simulate_growthform["Growth.FormTree:TreatmentShort"] - simulate_growthform[,"Growth.FormTree:TreatmentLong"])^2) /3)

summary_one_step_level1_3 = c(slope_level1_3, SE_slope = sd(slope_reps_level1_3[,1]))

summary_one_step_level1_3
```
*END OF SCRIPT*

