---
title: "Phylogenetic analysis on Ash's data"
output: html_document:
  keep_md:yes
---

Phylogenetic Analyses to test phylogentic signal in photoperiod sensitivity in germination for the manuscript: Jagdish et al. (In Review) - Shining a light on patterns of photoperiod sensitivty in seed germination across latitudes, ecosystems and functional traits

Step 1: Load libraries required
```{r}
library(dplyr)
library(devtools)
library(V.PhyloMaker)
library(ggplot2)
library(nlme)
library(phytools)
library(ggtree)
```

Step 2: read in data
- Note for a phylogenetic analysis we need to make sure we have three columns with these exact names - "species", "genus", "family" (being aware of case)
- species will be a column of things that have the long species name, e.g. Banksia serrata
- genus will be a column of JUST the genus name, same e.g. Banksia
- family is the family of the species, same e.g. Proteacea

```{r}
ashdata <- read.csv("LessThan5Phylo.csv")
```

Create a data frame with ONLY information about species, genus and family

```{r}
ashspecieslist <- select(ashdata, "species", "genus", "family")
```

Getting our tree
we ran the following code which extracts a tree of JUST OUR species
- note that GBOTB.extended is the default tree, it is the one created by Smith and Brown, 2018 with updated phylogenies
- output.sp.list = TRUE will mean that our tree will also spit out a list of what the analysis did to each species along the way, sometimes it bound the species to a tip in the tree, sometimes it prunes the species or sometimes it fails to bind the species to the backbone phylogeny - it is a good idea to check this list, because sometimes the "fail" is because there's a spelling error in the species/genus/family name
- output.tree = TRUE will allow the analysis to spit out a pretty little tree of our species
- scenarios is the choice we make about how to deal with species that are new and DON'T occur in the mega-tree. Scenario 3 ("S3"), I BELIEVE personally is the best way to deal with this - see Qian and Jin 2019 and Qian and Jin 2016 for a breakdown of the way each scenario works :)

```{r}
Phyloanalysis <- phylo.maker(ashspecieslist, tree = GBOTB.extended, output.sp.list = TRUE, output.tree = TRUE, scenarios = "S3")

ashtree <- Phyloanalysis$scenario.3 #creating just your tree (using scenario 3)
```

Plot that phylogeny to get a pretty tree diagram

```{r}
ashstree <- ggtree(ashtree,size=0.6) + geom_tiplab(size=3)
plot(ashstree)

#And save that tree above 

ggsave(filename = "ashtree.tiff", plot = ashstree, width = 12, height = 8, units = "in")

#but I took from phylo.plot tree to match the tip labels

plot.phylo(ashtree, cex = 0.5)


```


Now running a test for a phylogenetic signal

1. Make sure the branch labels (ie our species) match in the tree AND in our data frame

```{r}
# add a column with species' names with an underscore in them (because that's what V.phylomaker does to the species labels)
Species_ <- gsub(" ", "_", ashdata$species)
ashdata <- cbind(ashdata, Species_)

#make this column the row names 
rownames(ashdata) <- ashdata[,18]
```

2. Turn photoperiod into a vector and add the species names to it

```{r}
PP <- as.vector(ashdata$PP.Sensitivity.Sign)
names(PP) <- ashdata$Species_
```

3. Run two analyses- one with lambda method and one with K method

```{r}
lambda <- phylosig(ashtree, PP, method="lambda", test=TRUE)
print(lambda)

K <- phylosig(ashtree, PP, method="K", test=TRUE)
print(K)
```

BOTH show that there isn't a phylogenetic signal in photoperiod



Now, Making a graph of your tree with the Photoperiod sensitivity to see if there's a pattern!

There's probably a wayyy easier way to do this but the phytools pacakge seems to be really buggy and I spent ages to no avail, so I'm doing it by hand haha.

Steps:
1. Make a list of the species names in the ORDER as they appear in your tree (so that our graph will match up with the correct order)

```{r}
specieslist <- as.data.frame(Phyloanalysis$scenario.3$tip.label) %>%
  rename(species = `Phyloanalysis$scenario.3$tip.label`)

specieslist$species <- gsub("_", " ", specieslist$species)

```

2. Merge with photoperiod sensitivty data

```{r}
photoperiod <- left_join(specieslist, ashdata, by = "species")
```

3. create graph

```{r}
##lock in order of species
photoperiod$species <- factor(photoperiod$species, levels = photoperiod$species)

#plot
PSbyPHYLOplot <- ggplot(photoperiod, aes(x=PP.Sensitivity.Sign, y=species, fill = as.factor(Significance))) + geom_col() +
  scale_fill_manual(values = c("grey", "lightskyblue")) +
  theme_classic() +
  theme(axis.text.y = element_text(face = "italic", hjust = 0)) +
  theme(axis.text.y=element_text(size=10)) +
  theme(legend.text = element_blank())
plot(PSbyPHYLOplot)

#save plot

ggsave(filename = "ashpsplot.tiff", plot =  PSbyPHYLOplot, device = "tiff", dpi = 100, width= 15, height= 25, units = "in")
```

4. I then stitched this bar plot with the tree in gimp as the species were the same order in both







